### 2017-02-09 paper.tex
Initial commit of paper

%% bare_conf.tex
%% V1.4b
%% 2015/08/26
%% by Michael Shell
%% See:
%% http://www.michaelshell.org/
%% for current contact information.
%%
%% This is a skeleton file demonstrating the use of IEEEtran.cls
%% (requires IEEEtran.cls version 1.8b or later) with an IEEE
%% conference paper.
%%
%% Support sites:
%% http://www.michaelshell.org/tex/ieeetran/
%% http://www.ctan.org/pkg/ieeetran
%% and
%% http://www.ieee.org/

%%*************************************************************************
%% Legal Notice:
%% This code is offered as-is without any warranty either expressed or
%% implied; without even the implied warranty of MERCHANTABILITY or
%% FITNESS FOR A PARTICULAR PURPOSE! 
%% User assumes all risk.
%% In no event shall the IEEE or any contributor to this code be liable for
%% any damages or losses, including, but not limited to, incidental,
%% consequential, or any other damages, resulting from the use or misuse
%% of any information contained here.
%%
%% All comments are the opinions of their respective authors and are not
%% necessarily endorsed by the IEEE.
%%
%% This work is distributed under the LaTeX Project Public License (LPPL)
%% ( http://www.latex-project.org/ ) version 1.3, and may be freely used,
%% distributed and modified. A copy of the LPPL, version 1.3, is included
%% in the base LaTeX documentation of all distributions of LaTeX released
%% 2003/12/01 or later.
%% Retain all contribution notices and credits.
%% ** Modified files should be clearly indicated as such, including  **
%% ** renaming them and changing author support contact information. **
%%*************************************************************************

% *** Authors should verify (and, if needed, correct) their LaTeX system  ***
% *** with the testflow diagnostic prior to trusting their LaTeX platform ***
% *** with production work. The IEEE's font choices and paper sizes can   ***
% *** trigger bugs that do not appear when using other class files.       ***                          ***
% The testflow support page is at:
% http://www.michaelshell.org/tex/testflow/

\documentclass[conference]{IEEEtran}

\usepackage{cite}

% *** GRAPHICS RELATED PACKAGES ***
%
\ifCLASSINFOpdf
  % \usepackage[pdftex]{graphicx}
  % declare the path(s) where your graphic files are
  % \graphicspath{{../pdf/}{../jpeg/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
  % \DeclareGraphicsExtensions{.pdf,.jpeg,.png}
\else
  % or other class option (dvipsone, dvipdf, if not using dvips). graphicx
  % will default to the driver specified in the system graphics.cfg if no
  % driver is specified.
  % \usepackage[dvips]{graphicx}
  % declare the path(s) where your graphic files are
  % \graphicspath{{../eps/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
  % \DeclareGraphicsExtensions{.eps}
\fi
% graphicx was written by David Carlisle and Sebastian Rahtz. It is
% required if you want graphics, photos, etc. graphicx.sty is already
% installed on most LaTeX systems. The latest version and documentation
% can be obtained at: 
% http://www.ctan.org/pkg/graphicx
% Another good source of documentation is "Using Imported Graphics in
% LaTeX2e" by Keith Reckdahl which can be found at:
% http://www.ctan.org/pkg/epslatex
%
% latex, and pdflatex in dvi mode, support graphics in encapsulated
% postscript (.eps) format. pdflatex in pdf mode supports graphics
% in .pdf, .jpeg, .png and .mps (metapost) formats. Users should ensure
% that all non-photo figures use a vector format (.eps, .pdf, .mps) and
% not a bitmapped formats (.jpeg, .png). The IEEE frowns on bitmapped formats
% which can result in "jaggedy"/blurry rendering of lines and letters as
% well as large increases in file sizes.
%
% You can find documentation about the pdfTeX application at:
% http://www.tug.org/applications/pdftex

% *** SPECIALIZED LIST PACKAGES ***
%
%\usepackage{algorithmic}
% algorithmic.sty was written by Peter Williams and Rogerio Brito.
% This package provides an algorithmic environment fo describing algorithms.
% You can use the algorithmic environment in-text or within a figure
% environment to provide for a floating algorithm. Do NOT use the algorithm
% floating environment provided by algorithm.sty (by the same authors) or
% algorithm2e.sty (by Christophe Fiorio) as the IEEE does not use dedicated
% algorithm float types and packages that provide these will not provide
% correct IEEE style captions. The latest version and documentation of
% algorithmic.sty can be obtained at:
% http://www.ctan.org/pkg/algorithms
% Also of interest may be the (relatively newer and more customizable)
% algorithmicx.sty package by Szasz Janos:
% http://www.ctan.org/pkg/algorithmicx

% *** ALIGNMENT PACKAGES ***
%
%\usepackage{array}
% Frank Mittelbach's and David Carlisle's array.sty patches and improves
% the standard LaTeX2e array and tabular environments to provide better
% appearance and additional user controls. As the default LaTeX2e table
% generation code is lacking to the point of almost being broken with
% respect to the quality of the end results, all users are strongly
% advised to use an enhanced (at the very least that provided by array.sty)
% set of table tools. array.sty is already installed on most systems. The
% latest version and documentation can be obtained at:
% http://www.ctan.org/pkg/array

% IEEEtran contains the IEEEeqnarray family of commands that can be used to
% generate multiline equations as well as matrices, tables, etc., of high
% quality.

% *** SUBFIGURE PACKAGES ***
%\ifCLASSOPTIONcompsoc
%  \usepackage[caption=false,font=normalsize,labelfont=sf,textfont=sf]{subfig}
%\else
%  \usepackage[caption=false,font=footnotesize]{subfig}
%\fi
% subfig.sty, written by Steven Douglas Cochran, is the modern replacement
% for subfigure.sty, the latter of which is no longer maintained and is
% incompatible with some LaTeX packages including fixltx2e. However,
% subfig.sty requires and automatically loads Axel Sommerfeldt's caption.sty
% which will override IEEEtran.cls' handling of captions and this will result
% in non-IEEE style figure/table captions. To prevent this problem, be sure
% and invoke subfig.sty's "caption=false" package option (available since
% subfig.sty version 1.3, 2005/06/28) as this is will preserve IEEEtran.cls
% handling of captions.
% Note that the Computer Society format requires a larger sans serif font
% than the serif footnote size font used in traditional IEEE formatting
% and thus the need to invoke different subfig.sty package options depending
% on whether compsoc mode has been enabled.
%
% The latest version and documentation of subfig.sty can be obtained at:
% http://www.ctan.org/pkg/subfig

% *** FLOAT PACKAGES ***
%
%\usepackage{fixltx2e}
% fixltx2e, the successor to the earlier fix2col.sty, was written by
% Frank Mittelbach and David Carlisle. This package corrects a few problems
% in the LaTeX2e kernel, the most notable of which is that in current
% LaTeX2e releases, the ordering of single and double column floats is not
% guaranteed to be preserved. Thus, an unpatched LaTeX2e can allow a
% single column figure to be placed prior to an earlier double column
% figure.
% Be aware that LaTeX2e kernels dated 2015 and later have fixltx2e.sty's
% corrections already built into the system in which case a warning will
% be issued if an attempt is made to load fixltx2e.sty as it is no longer
% needed.
% The latest version and documentation can be found at:
% http://www.ctan.org/pkg/fixltx2e

%\usepackage{stfloats}
% stfloats.sty was written by Sigitas Tolusis. This package gives LaTeX2e
% the ability to do double column floats at the bottom of the page as well
% as the top. (e.g., "\begin{figure*}[!b]" is not normally possible in
% LaTeX2e). It also provides a command:
%\fnbelowfloat
% to enable the placement of footnotes below bottom floats (the standard
% LaTeX2e kernel puts them above bottom floats). This is an invasive package
% which rewrites many portions of the LaTeX2e float routines. It may not work
% with other packages that modify the LaTeX2e float routines. The latest
% version and documentation can be obtained at:
% http://www.ctan.org/pkg/stfloats
% Do not use the stfloats baselinefloat ability as the IEEE does not allow
% \baselineskip to stretch. Authors submitting work to the IEEE should note
% that the IEEE rarely uses double column equations and that authors should try
% to avoid such use. Do not be tempted to use the cuted.sty or midfloat.sty
% packages (also by Sigitas Tolusis) as the IEEE does not format its papers in
% such ways.
% Do not attempt to use stfloats with fixltx2e as they are incompatible.
% Instead, use Morten Hogholm'a dblfloatfix which combines the features
% of both fixltx2e and stfloats:
%
% \usepackage{dblfloatfix}
% The latest version can be found at:
% http://www.ctan.org/pkg/dblfloatfix

% *** PDF, URL AND HYPERLINK PACKAGES ***
%
\usepackage{url}
% url.sty was written by Donald Arseneau. It provides better support for
% handling and breaking URLs. url.sty is already installed on most LaTeX
% systems. The latest version and documentation can be obtained at:
% http://www.ctan.org/pkg/url
% Basically, \url{my_url_here}.

% *** Do not adjust lengths that control margins, column widths, etc. ***
% *** Do not use packages that alter fonts (such as pslatex).         ***
% There should be no need to do such things with IEEEtran.cls V1.6 and later.
% (Unless specifically asked to do so by the journal or conference you plan
% to submit to, of course. )

% correct bad hyphenation here
\hyphenation{op-tical net-works semi-conduc-tor}

\begin{document}
%
% paper title
% Titles are generally capitalized except for words such as a, an, and, as,
% at, but, by, for, in, nor, of, on, or, the, to and up, which are usually
% not capitalized unless they are the first or last word of the title.
% Linebreaks \\ can be used within to get better formatting as desired.
% Do not put math or special symbols in the title.
\title{fl0w 2.0 - a development environment for the\\ KIPR Wallaby}

% author names and affiliations
% use a multiple column layout for up to three different
% affiliations
\author{\IEEEauthorblockN{Philip Trauner}
\IEEEauthorblockA{School of Computer Engineering\\
HTBLuVA Wiener Neustadt\\
Email: philip.trauner@arztpraxis.io}
\and
\IEEEauthorblockN{Christoph Heiss}
\IEEEauthorblockA{School of Computer Engineering\\
HTBLuVA Wiener Neustadt\\
Email: me@christoph-heiss.me}}

\maketitle

\begin{abstract}
This publication introduces fl0w, an alternative\\ development environment for the KIPR Wallaby.\\ The aim of fl0w is to improve the robotics development\\ experience. It focuses on the components that make up fl0w, namely a file synchronization protocol that maintains a consistent state across all connected controllers, a route based and data type preserving network protocol with peer-to-peer piping capabilities, a discovery protocol that connects all controllers together automatically, a Sublime Text \cite{Sublime Text 3:Sublime HQ} plugin which enables in-line sensor readouts, program execution, program editing, and keyboard shortcuts, and a browser-based management front-end to manage the fl0w fleet.\\
\end{abstract}

\begin{IEEEkeywords}
file synchronization, networking, LAN discovery
\end{IEEEkeywords}

\section{Introduction}
% no \IEEEPARstart
This demo file is intended to serve as a ``starter file''
for IEEE conference papers produced under \LaTeX\ using
IEEEtran.cls version 1.8b and later.
% You must have at least 2 lines in the paragraph with the drop letter
% (should never be an issue)
I wish you the best of success.

\hfill mds

\hfill August 26, 2015

\subsection{Subsection Heading Here}
Subsection text here.

\subsubsection{Subsubsection Heading Here}
Subsubsection text here.

% An example of a floating figure using the graphicx package.
% Note that \label must occur AFTER (or within) \caption.
% For figures, \caption should occur after the \includegraphics.
% Note that IEEEtran v1.7 and later has special internal code that
% is designed to preserve the operation of \label within \caption
% even when the captionsoff option is in effect. However, because
% of issues like this, it may be the safest practice to put all your
% \label just after \caption rather than within \caption{}.
%
% Reminder: the "draftcls" or "draftclsnofoot", not "draft", class
% option should be used if it is desired that the figures are to be
% displayed while in draft mode.
%
%\begin{figure}[!t]
%\centering
%\includegraphics[width=2.5in]{myfigure}
% where an .eps filename suffix will be assumed under latex, 
% and a .pdf suffix will be assumed for pdflatex; or what has been declared
% via \DeclareGraphicsExtensions.
%\caption{Simulation results for the network.}
%\label{fig_sim}
%\end{figure}

% Note that the IEEE typically puts floats only at the top, even when this
% results in a large percentage of a column being occupied by floats.

% An example of a double column floating figure using two subfigures.
% (The subfig.sty package must be loaded for this to work.)
% The subfigure \label commands are set within each subfloat command,
% and the \label for the overall figure must come after \caption.
% \hfil is used as a separator to get equal spacing.
% Watch out that the combined width of all the subfigures on a 
% line do not exceed the text width or a line break will occur.
%
%\begin{figure*}[!t]
%\centering
%\subfloat[Case I]{\includegraphics[width=2.5in]{box}%
%\label{fig_first_case}}
%\hfil
%\subfloat[Case II]{\includegraphics[width=2.5in]{box}%
%\label{fig_second_case}}
%\caption{Simulation results for the network.}
%\label{fig_sim}
%\end{figure*}
%
% Note that often IEEE papers with subfigures do not employ subfigure
% captions (using the optional argument to \subfloat[]), but instead will
% reference/describe all of them (a), (b), etc., within the main caption.
% Be aware that for subfig.sty to generate the (a), (b), etc., subfigure
% labels, the optional argument to \subfloat must be present. If a
% subcaption is not desired, just leave its contents blank,
% e.g., \subfloat[].

% An example of a floating table. Note that, for IEEE style tables, the
% \caption command should come BEFORE the table and, given that table
% captions serve much like titles, are usually capitalized except for words
% such as a, an, and, as, at, but, by, for, in, nor, of, on, or, the, to
% and up, which are usually not capitalized unless they are the first or
% last word of the caption. Table text will default to \footnotesize as
% the IEEE normally uses this smaller font for tables.
% The \label must come after \caption as always.
%
%\begin{table}[!t]
%% increase table row spacing, adjust to taste
%\renewcommand{\arraystretch}{1.3}
% if using array.sty, it might be a good idea to tweak the value of
% \extrarowheight as needed to properly center the text within the cells
%\caption{An Example of a Table}
%\label{table_example}
%\centering
%% Some packages, such as MDW tools, offer better commands for making tables
%% than the plain LaTeX2e tabular which is used here.
%\begin{tabular}{|c||c|}
%\hline
%One & Two\\
%\hline
%Three & Four\\
%\hline
%\end{tabular}
%\end{table}

% Note that the IEEE does not put floats in the very first column
% - or typically anywhere on the first page for that matter. Also,
% in-text middle ("here") positioning is typically not used, but it
% is allowed and encouraged for Computer Society conferences (but
% not Computer Society journals). Most IEEE journals/conferences use
% top floats exclusively. 
% Note that, LaTeX2e, unlike IEEE journals/conferences, places
% footnotes above bottom floats. This can be corrected via the
% \fnbelowfloat command of the stfloats package.

\section{Conclusion}
The conclusion goes here.

% conference papers do not normally have an appendix

% use section* for acknowledgment
\section*{Acknowledgment}
The authors would like to thank the robotics team robot0nfire: Nico Kratky, Nico Leidenfrost,\\ Sebastian Schaffler, Christine Zeh, Sascha Zemann;\\ Dr. Michael Stifter for making the existence of our team possible; Daniel Maximilian Swoboda for answering all paper related questions; the KIPR development team without whom the Wallaby Controller would not exist.

% trigger a \newpage just before the given reference
% number - used to balance the columns on the last page
% adjust value as needed - may need to be readjusted if
% the document is modified later
%\IEEEtriggeratref{8}
% The "triggered" command can be changed if desired:
%\IEEEtriggercmd{\enlargethispage{-5in}}

% references section

% can use a bibliography generated by BibTeX as a .bbl file
% BibTeX documentation can be easily obtained at:
% http://mirror.ctan.org/biblio/bibtex/contrib/doc/
% The IEEEtran BibTeX style support page is at:
% http://www.michaelshell.org/tex/ieeetran/bibtex/
%\bibliographystyle{IEEEtran}
% argument is your BibTeX string definitions and bibliography database(s)
%\bibliography{IEEEabrv,../bib/paper}
%
% <OR> manually copy in the resultant .bbl file
% set second argument of \begin to the number of references
% (used to reserve space for the reference number labels box)
\begin{thebibliography}{1}

\bibitem{Sublime Text 3:Sublime HQ}
Sublime HQ, \emph{Sublime Text 3}, \url{https://www.sublimetext.com/3},\\ product page,
accessed February 9th 2017

\end{thebibliography}

% that's all folks
\end{document}

### 2017-02-09 paper.tex
Added introduction, implementation as well as components section
Components sections is still work in progress

@@
 \begin{abstract}
-This publication introduces fl0w, an alternative\\ development environment for the KIPR Wallaby.\\ The aim of fl0w is to improve the robotics development\\ experience.
-It focuses on the components that make up fl0w, namely a file synchronization protocol that maintains a consistent state across all connected controllers, a route based and data type preserving network protocol with peer-to-peer piping capabilities, a discovery protocol that connects all controllers together automatically, a Sublime Text \cite{Sublime Text 3:Sublime HQ} plugin which enables in-line sensor readouts, program execution, program editing, and keyboard shortcuts, and a browser-based management front-end to manage the fl0w fleet.\\
+This publication introduces fl0w, an alternative\\ development environment for the KIPR Wallaby.\\ The aim of fl0w is to improve the robotics program development experience.
+It focuses on the components that make up fl0w, namely a file synchronization protocol that maintains a consistent state across all connected controllers, a route based and data type preserving network protocol with peer-to-peer piping capabilities, a discovery protocol that connects all controllers together automatically, a Sublime Text 3\cite{Sublime Text 3:Sublime HQ} plugin which enables in-line sensor readouts, program execution, program editing, and keyboard shortcuts, and a browser-based management front-end to manage the controller fleet.\\
 \end{abstract}
@@
 \begin{IEEEkeywords}
-file synchronization, networking, LAN discovery
+file synchronization, networking, LAN discovery, development environment
 \end{IEEEkeywords}
@@
 \section{Introduction}
-% no \IEEEPARstart
-This demo file is intended to serve as a ``starter file''
-for IEEE conference papers produced under \LaTeX\ using
-IEEEtran.cls version 1.8b and later.
-% You must have at least 2 lines in the paragraph with the drop letter
-% (should never be an issue)
-I wish you the best of success.
+fl0w was developed out of a need for a fast, reliable and wireless workflow solution that can compete with the currently available offerings like Harrogate\cite{Harrogate:KIPR}.
+Its goals are to transform the connected controllers to a redundant fleet of logical units that share the same binaries and source code, real-time in-line sensor readouts, and a management layer inside the text editor as well as a browser-based interface.
 
-\hfill mds
+\section{Implementation}
+All fl0w components emphasize shared code and are therefor written in Python 3.3.6\cite{Python 3.3.6:Python Foundation} to remain compatible with the Sublime Text 3\cite{Sublime Text 3:Sublime HQ} plugin environment.
+Python was chosen as the implementation language for fl0w because of its rich standard library and its lightweight virtual machine that can run on a Wallaby controller with acceptable speed.
+A pre-compiled version of Python 3.3.6 \cite{Python 3.3.6:Python Foundation} is bundled with the fl0w installer because it is not present on the Wallaby by default.
+All fl0w components are designed as libraries to allow for integration into other projects.
 
-\hfill August 26, 2015
+\section{Components}
+\subsection{undergr0und}
+undergr0und\cite{undergr0und:Philip Trauner} is an asynchronous route based and data type preserving network protocol with peer-to-peer piping capabilities.
+The Python\cite{Python 3.3.6:Python Foundation} version is built on top of a fork of ws4py\cite{ws4py:Philip Trauner} and the JavaScript version utilizes regular WebSockets\cite{The WebSocket Protocol:A.
+Melnikov}.
+It was created to mitigate the problems fl0ws explorative development style created.
+Instead of one monolithic network protocol, undergr0und consists of many small sub protocols.
+This was done because all monolithic design would at some point become too inconsistent.
+undergr0und\cite{undergr0und:Philip Trauner} manages itself through its own capabilities.
 
-\subsection{Subsection Heading Here}
-Subsection text here.
-
-\subsubsection{Subsubsection Heading Here}
-Subsubsection text here.
+\subsubsection{Pipes}
+Pipes are client peer-to-peer messages piped through the server.
 
@@
 
+\section*{Acknowledgment}
+
 % trigger a \newpage just before the given reference
@@
 
+\bibitem{Harrogate:KIPR}
+KIPR, \emph{Harrogate}, \url{https://github.com/kipr/harrogate},\\ source code,
+accessed February 9th 2017
+
+\bibitem{Python 3.3.6:Python Foundation}
+Python Foundation, \emph{Python 3.3.6}, \url{https://www.python.org/downloads/release/python-336/}, source code, accessed February 9th 2017
+
+\bibitem{undergr0und:Philip Trauner}
+Philip Trauner, \emph{undergr0und}, \url{https://github.com/robot0nfire/fl0w/wiki/undergr0und}, implementation notes, accessed February 9th 2017
+
+\bibitem{ws4py:Philip Trauner}
+Philip Trauner, \emph{ws4py}, \url{https://github.com/robot0nfire/ws4py}, source code, accessed February 9th 2017
+
+\bibitem{The WebSocket Protocol:A. Melnikov}
+A. Melnikov, \emph{The WebSocket Protocol}, \url{https://tools.ietf.org/html/rfc6455}, implementation notes, accessed February 9th 2017
+
 \end{thebibliography}

### 2017-02-09 paper.tex
Removed IEEE comments, initial commit of undergr0und writeup

@@
-%% bare_conf.tex
-%% V1.4b
-%% 2015/08/26
-%% by Michael Shell
-%% See:
-%% http://www.michaelshell.org/
-%% for current contact information.
-%%
-%% This is a skeleton file demonstrating the use of IEEEtran.cls
-%% (requires IEEEtran.cls version 1.8b or later) with an IEEE
-%% conference paper.
-%%
-%% Support sites:
-%% http://www.michaelshell.org/tex/ieeetran/
-%% http://www.ctan.org/pkg/ieeetran
-%% and
-%% http://www.ieee.org/
-
-%%*************************************************************************
-%% Legal Notice:
-%% This code is offered as-is without any warranty either expressed or
-%% implied; without even the implied warranty of MERCHANTABILITY or
-%% FITNESS FOR A PARTICULAR PURPOSE! 
-%% User assumes all risk.
-%% In no event shall the IEEE or any contributor to this code be liable for
-%% any damages or losses, including, but not limited to, incidental,
-%% consequential, or any other damages, resulting from the use or misuse
-%% of any information contained here.
-%%
-%% All comments are the opinions of their respective authors and are not
-%% necessarily endorsed by the IEEE.
-%%
-%% This work is distributed under the LaTeX Project Public License (LPPL)
-%% ( http://www.latex-project.org/ ) version 1.3, and may be freely used,
-%% distributed and modified. A copy of the LPPL, version 1.3, is included
-%% in the base LaTeX documentation of all distributions of LaTeX released
-%% 2003/12/01 or later.
-%% Retain all contribution notices and credits.
-%% ** Modified files should be clearly indicated as such, including  **
-%% ** renaming them and changing author support contact information. **
-%%*************************************************************************
-
-% *** Authors should verify (and, if needed, correct) their LaTeX system  ***
-% *** with the testflow diagnostic prior to trusting their LaTeX platform ***
-% *** with production work. The IEEE's font choices and paper sizes can   ***
-% *** trigger bugs that do not appear when using other class files.       ***                          ***
-% The testflow support page is at:
-% http://www.michaelshell.org/tex/testflow/
-
 \documentclass[conference]{IEEEtran}
-
-\usepackage{cite}
-
-% *** GRAPHICS RELATED PACKAGES ***
-%
-\ifCLASSINFOpdf
-  % \usepackage[pdftex]{graphicx}
-  % declare the path(s) where your graphic files are
-  % \graphicspath{{../pdf/}{../jpeg/}}
-  % and their extensions so you won't have to specify these with
-  % every instance of \includegraphics
-  % \DeclareGraphicsExtensions{.pdf,.jpeg,.png}
-\else
-  % or other class option (dvipsone, dvipdf, if not using dvips). graphicx
-  % will default to the driver specified in the system graphics.cfg if no
-  % driver is specified.
-  % \usepackage[dvips]{graphicx}
-  % declare the path(s) where your graphic files are
-  % \graphicspath{{../eps/}}
-  % and their extensions so you won't have to specify these with
-  % every instance of \includegraphics
-  % \DeclareGraphicsExtensions{.eps}
-\fi
-% graphicx was written by David Carlisle and Sebastian Rahtz. It is
-% required if you want graphics, photos, etc. graphicx.sty is already
-% installed on most LaTeX systems. The latest version and documentation
-% can be obtained at: 
-% http://www.ctan.org/pkg/graphicx
-% Another good source of documentation is "Using Imported Graphics in
-% LaTeX2e" by Keith Reckdahl which can be found at:
-% http://www.ctan.org/pkg/epslatex
-%
-% latex, and pdflatex in dvi mode, support graphics in encapsulated
-% postscript (.eps) format. pdflatex in pdf mode supports graphics
-% in .pdf, .jpeg, .png and .mps (metapost) formats. Users should ensure
-% that all non-photo figures use a vector format (.eps, .pdf, .mps) and
-% not a bitmapped formats (.jpeg, .png). The IEEE frowns on bitmapped formats
-% which can result in "jaggedy"/blurry rendering of lines and letters as
-% well as large increases in file sizes.
-%
-% You can find documentation about the pdfTeX application at:
-% http://www.tug.org/applications/pdftex
-
-% *** SPECIALIZED LIST PACKAGES ***
-%
-%\usepackage{algorithmic}
-% algorithmic.sty was written by Peter Williams and Rogerio Brito.
-% This package provides an algorithmic environment fo describing algorithms.
-% You can use the algorithmic environment in-text or within a figure
-% environment to provide for a floating algorithm. Do NOT use the algorithm
-% floating environment provided by algorithm.sty (by the same authors) or
-% algorithm2e.sty (by Christophe Fiorio) as the IEEE does not use dedicated
-% algorithm float types and packages that provide these will not provide
-% correct IEEE style captions. The latest version and documentation of
-% algorithmic.sty can be obtained at:
-% http://www.ctan.org/pkg/algorithms
-% Also of interest may be the (relatively newer and more customizable)
-% algorithmicx.sty package by Szasz Janos:
-% http://www.ctan.org/pkg/algorithmicx
-
-% *** ALIGNMENT PACKAGES ***
-%
-%\usepackage{array}
-% Frank Mittelbach's and David Carlisle's array.sty patches and improves
-% the standard LaTeX2e array and tabular environments to provide better
-% appearance and additional user controls. As the default LaTeX2e table
-% generation code is lacking to the point of almost being broken with
-% respect to the quality of the end results, all users are strongly
-% advised to use an enhanced (at the very least that provided by array.sty)
-% set of table tools. array.sty is already installed on most systems. The
-% latest version and documentation can be obtained at:
-% http://www.ctan.org/pkg/array
-
-% IEEEtran contains the IEEEeqnarray family of commands that can be used to
-% generate multiline equations as well as matrices, tables, etc., of high
-% quality.
-
-% *** SUBFIGURE PACKAGES ***
-%\ifCLASSOPTIONcompsoc
-%  \usepackage[caption=false,font=normalsize,labelfont=sf,textfont=sf]{subfig}
-%\else
-%  \usepackage[caption=false,font=footnotesize]{subfig}
-%\fi
-% subfig.sty, written by Steven Douglas Cochran, is the modern replacement
-% for subfigure.sty, the latter of which is no longer maintained and is
-% incompatible with some LaTeX packages including fixltx2e. However,
-% subfig.sty requires and automatically loads Axel Sommerfeldt's caption.sty
-% which will override IEEEtran.cls' handling of captions and this will result
-% in non-IEEE style figure/table captions. To prevent this problem, be sure
-% and invoke subfig.sty's "caption=false" package option (available since
-% subfig.sty version 1.3, 2005/06/28) as this is will preserve IEEEtran.cls
-% handling of captions.
-% Note that the Computer Society format requires a larger sans serif font
-% than the serif footnote size font used in traditional IEEE formatting
-% and thus the need to invoke different subfig.sty package options depending
-% on whether compsoc mode has been enabled.
-%
-% The latest version and documentation of subfig.sty can be obtained at:
-% http://www.ctan.org/pkg/subfig
-
-% *** FLOAT PACKAGES ***
-%
-%\usepackage{fixltx2e}
-% fixltx2e, the successor to the earlier fix2col.sty, was written by
-% Frank Mittelbach and David Carlisle. This package corrects a few problems
-% in the LaTeX2e kernel, the most notable of which is that in current
-% LaTeX2e releases, the ordering of single and double column floats is not
-% guaranteed to be preserved. Thus, an unpatched LaTeX2e can allow a
-% single column figure to be placed prior to an earlier double column
-% figure.
-% Be aware that LaTeX2e kernels dated 2015 and later have fixltx2e.sty's
-% corrections already built into the system in which case a warning will
-% be issued if an attempt is made to load fixltx2e.sty as it is no longer
-% needed.
-% The latest version and documentation can be found at:
-% http://www.ctan.org/pkg/fixltx2e
-
-%\usepackage{stfloats}
-% stfloats.sty was written by Sigitas Tolusis. This package gives LaTeX2e
-% the ability to do double column floats at the bottom of the page as well
-% as the top. (e.g., "\begin{figure*}[!b]" is not normally possible in
-% LaTeX2e). It also provides a command:
-%\fnbelowfloat
-% to enable the placement of footnotes below bottom floats (the standard
-% LaTeX2e kernel puts them above bottom floats). This is an invasive package
-% which rewrites many portions of the LaTeX2e float routines. It may not work
-% with other packages that modify the LaTeX2e float routines. The latest
-% version and documentation can be obtained at:
-% http://www.ctan.org/pkg/stfloats
-% Do not use the stfloats baselinefloat ability as the IEEE does not allow
-% \baselineskip to stretch. Authors submitting work to the IEEE should note
-% that the IEEE rarely uses double column equations and that authors should try
-% to avoid such use. Do not be tempted to use the cuted.sty or midfloat.sty
-% packages (also by Sigitas Tolusis) as the IEEE does not format its papers in
-% such ways.
-% Do not attempt to use stfloats with fixltx2e as they are incompatible.
-% Instead, use Morten Hogholm'a dblfloatfix which combines the features
-% of both fixltx2e and stfloats:
-%
-% \usepackage{dblfloatfix}
-% The latest version can be found at:
-% http://www.ctan.org/pkg/dblfloatfix
-
-% *** PDF, URL AND HYPERLINK PACKAGES ***
-%
-\usepackage{url}
-% url.sty was written by Donald Arseneau. It provides better support for
-% handling and breaking URLs. url.sty is already installed on most LaTeX
-% systems. The latest version and documentation can be obtained at:
-% http://www.ctan.org/pkg/url
-% Basically, \url{my_url_here}.
-
-% *** Do not adjust lengths that control margins, column widths, etc. ***
-% *** Do not use packages that alter fonts (such as pslatex).         ***
-% There should be no need to do such things with IEEEtran.cls V1.6 and later.
-% (Unless specifically asked to do so by the journal or conference you plan
-% to submit to, of course. )
 
@@
 
+\usepackage{float}
+\usepackage[utf8]{inputenc}
+\usepackage{url}
+\usepackage{array}
+\usepackage{cite}
+
+% Centered columns
+\newcolumntype{V}{>{\bf\centering\arraybackslash} m{.2\linewidth} }
+
+% Default fixed font does not support bold face
+\DeclareFixedFont{\ttb}{T1}{txtt}{bx}{n}{12} % for bold
+\DeclareFixedFont{\ttm}{T1}{txtt}{m}{n}{12}  % for normal
+
+% Custom colors
+\usepackage{color}
+\definecolor{deepblue}{rgb}{0,0,0.5}
+\definecolor{deepred}{rgb}{0.6,0,0}
+\definecolor{deepgreen}{rgb}{0,0.5,0}
+
+\usepackage{listings}
+
+% Python style for highlighting
+\newcommand\pythonstyle{\lstset{
+language=Python,
+basicstyle=\ttm,
+otherkeywords={self},
+keywordstyle=\ttb\color{deepblue},
+emphstyle=\ttb\color{deepred},
+stringstyle=\color{deepgreen},
+frame=tb,
+showstringspaces=false
+}}
+
+% Python environment
+\lstnewenvironment{python}[1][]
+{
+\pythonstyle
+\lstset{#1}
+}
+{}
+
 \begin{document}
-%
-% paper title
-% Titles are generally capitalized except for words such as a, an, and, as,
-% at, but, by, for, in, nor, of, on, or, the, to and up, which are usually
-% not capitalized unless they are the first or last word of the title.
-% Linebreaks \\ can be used within to get better formatting as desired.
-% Do not put math or special symbols in the title.
+
 \title{fl0w 2.0 - a development environment for the\\ KIPR Wallaby}
-
-% author names and affiliations
-% use a multiple column layout for up to three different
-% affiliations
 \author{\IEEEauthorblockN{Philip Trauner}
@@
 undergr0und\cite{undergr0und:Philip Trauner} is an asynchronous route based and data type preserving network protocol with peer-to-peer piping capabilities. 
+It automatically converts data into a transferable format and prepends binary headers to allow for reconstruction on the other end.
+
+\begin{figure}[H]
+\centering
+	\begin{tabular}{*{3}{V}}
+		Data type & Route ID & Data \\ \hline
+		1 & 2 & * \\
+	\end{tabular}
+	\caption{The binary encoding of undergr0und (in bytes)}
+\label{fig:undergr0und_header}
+\end{figure}
+
 The Python\cite{Python 3.3.6:Python Foundation} version is built on top of a fork of ws4py\cite{ws4py:Philip Trauner} and the JavaScript version utilizes regular WebSockets\cite{The WebSocket Protocol:A.
-Melnikov}.
+Melnikov} (in arraybuffer mode).
 It was created to mitigate the problems fl0ws explorative development style created.
 Instead of one monolithic network protocol, undergr0und consists of many small sub protocols.
-This was done because all monolithic design would at some point become too inconsistent.
-undergr0und\cite{undergr0und:Philip Trauner} manages itself through its own capabilities.
+This was done because all monolithic designs became too inconsistent.
+undergr0und\cite{undergr0und:Philip Trauner} manages itself through its own concepts.
 
-\subsubsection{Pipes}
-Pipes are client peer-to-peer messages piped through the server.
+\subsubsection{Exchange table}
+To reduce the required additional bandwidth per message that is introduced with variable character count routes a numbered route lookup table is generated on startup by clients and the server.
+Before any communication takes place these lookup tables are exchanged.
+Route ID 0 is reserved by undergr0und\cite{undergr0und:Philip Trauner} for self management purposes.
 
-% An example of a floating figure using the graphicx package.
-% Note that \label must occur AFTER (or within) \caption.
-% For figures, \caption should occur after the \includegraphics.
-% Note that IEEEtran v1.7 and later has special internal code that
-% is designed to preserve the operation of \label within \caption
-% even when the captionsoff option is in effect. However, because
-% of issues like this, it may be the safest practice to put all your
-% \label just after \caption rather than within \caption{}.
-%
-% Reminder: the "draftcls" or "draftclsnofoot", not "draft", class
-% option should be used if it is desired that the figures are to be
-% displayed while in draft mode.
-%
-%\begin{figure}[!t]
-%\centering
-%\includegraphics[width=2.5in]{myfigure}
-% where an .eps filename suffix will be assumed under latex, 
-% and a .pdf suffix will be assumed for pdflatex; or what has been declared
-% via \DeclareGraphicsExtensions.
-%\caption{Simulation results for the network.}
-%\label{fig_sim}
-%\end{figure}
+\begin{figure}[H]
+\centering
+\begin{python}
+>>> routes = {"echo": Echo(), 
+...    "help": Help()}
+>>> create_exchange_map(routes)
+{0: "meta", 1: "echo", 2: "help"}
+\end{python}
+\caption{Creation of exchange maps}
+\end{figure}
 
-% Note that the IEEE typically puts floats only at the top, even when this
-% results in a large percentage of a column being occupied by floats.
+\subsubsection{Data type preservation}
+The original type of the data segment is present inside the header $($see Figure ~\ref{fig:undergr0und_header}$)$ to accurately reconstruct sent data on the other end.
+JSON\cite{JSON:T.
+Bray Ed.} is used to transfer lists and dictionaries, and regular ASCII encoded strings are utilized to transfer integers, floats, null/none types and strings.
 
-% An example of a double column floating figure using two subfigures.
-% (The subfig.sty package must be loaded for this to work.)
-% The subfigure \label commands are set within each subfloat command,
-% and the \label for the overall figure must come after \caption.
-% \hfil is used as a separator to get equal spacing.
-% Watch out that the combined width of all the subfigures on a 
-% line do not exceed the text width or a line break will occur.
-%
-%\begin{figure*}[!t]
-%\centering
-%\subfloat[Case I]{\includegraphics[width=2.5in]{box}%
-%\label{fig_first_case}}
-%\hfil
-%\subfloat[Case II]{\includegraphics[width=2.5in]{box}%
-%\label{fig_second_case}}
-%\caption{Simulation results for the network.}
-%\label{fig_sim}
-%\end{figure*}
-%
-% Note that often IEEE papers with subfigures do not employ subfigure
-% captions (using the optional argument to \subfloat[]), but instead will
-% reference/describe all of them (a), (b), etc., within the main caption.
-% Be aware that for subfig.sty to generate the (a), (b), etc., subfigure
-% labels, the optional argument to \subfloat must be present. If a
-% subcaption is not desired, just leave its contents blank,
-% e.g., \subfloat[].
+\subsubsection{Route}
+A client$\,\to\,$server / server$\,\to\,$client construct.
 
-% An example of a floating table. Note that, for IEEE style tables, the
-% \caption command should come BEFORE the table and, given that table
-% captions serve much like titles, are usually capitalized except for words
-% such as a, an, and, as, at, but, by, for, in, nor, of, on, or, the, to
-% and up, which are usually not capitalized unless they are the first or
-% last word of the caption. Table text will default to \footnotesize as
-% the IEEE normally uses this smaller font for tables.
-% The \label must come after \caption as always.
-%
-%\begin{table}[!t]
-%% increase table row spacing, adjust to taste
-%\renewcommand{\arraystretch}{1.3}
-% if using array.sty, it might be a good idea to tweak the value of
-% \extrarowheight as needed to properly center the text within the cells
-%\caption{An Example of a Table}
-%\label{table_example}
-%\centering
-%% Some packages, such as MDW tools, offer better commands for making tables
-%% than the plain LaTeX2e tabular which is used here.
-%\begin{tabular}{|c||c|}
-%\hline
-%One & Two\\
-%\hline
-%Three & Four\\
-%\hline
-%\end{tabular}
-%\end{table}
-
-% Note that the IEEE does not put floats in the very first column
-% - or typically anywhere on the first page for that matter. Also,
-% in-text middle ("here") positioning is typically not used, but it
-% is allowed and encouraged for Computer Society conferences (but
-% not Computer Society journals). Most IEEE journals/conferences use
-% top floats exclusively. 
-% Note that, LaTeX2e, unlike IEEE journals/conferences, places
-% footnotes above bottom floats. This can be corrected via the
-% \fnbelowfloat command of the stfloats package.
+\subsubsection{Pipe}
+A client$\,\to\,$server$\,\to\,$client construct.
+Clients can be targeted with unique IDs that are generated randomly for all connected peers by the server.
+There is no predefined mechanism in the network protocol that exposed these peer IDs, the application using undergr0und\cite{undergr0und:Philip Trauner} has to provide a way of making them available.
+Pipe messages are packaged inside regular route messages with additional headers in the data segment.
+An optional server route called {\color{deepgreen}"pipe"} unpacks the regular and the extended headers and forwards the message to the targeted peer.
 
@@
 
-% conference papers do not normally have an appendix
-
-% use section* for acknowledgment
+% section* for acknowledgment
 \section*{Acknowledgment}
@@
 
-\section*{Acknowledgment}
-
-% trigger a \newpage just before the given reference
-% number - used to balance the columns on the last page
-% adjust value as needed - may need to be readjusted if
-% the document is modified later
-%\IEEEtriggeratref{8}
-% The "triggered" command can be changed if desired:
-%\IEEEtriggercmd{\enlargethispage{-5in}}
-
-% references section
-
-% can use a bibliography generated by BibTeX as a .bbl file
-% BibTeX documentation can be easily obtained at:
-% http://mirror.ctan.org/biblio/bibtex/contrib/doc/
-% The IEEEtran BibTeX style support page is at:
-% http://www.michaelshell.org/tex/ieeetran/bibtex/
-%\bibliographystyle{IEEEtran}
-% argument is your BibTeX string definitions and bibliography database(s)
-%\bibliography{IEEEabrv,../bib/paper}
-%
-% <OR> manually copy in the resultant .bbl file
-% set second argument of \begin to the number of references
-% (used to reserve space for the reference number labels box)
 \begin{thebibliography}{1}
@@
 \bibitem{The WebSocket Protocol:A. Melnikov}
-A. Melnikov, \emph{The WebSocket Protocol}, \url{https://tools.ietf.org/html/rfc6455}, implementation notes, accessed February 9th 2017
+A. Melnikov, \emph{The WebSocket Protocol}, \url{https://tools.ietf.org/html/rfc6455}, request for comment, accessed February 9th 2017
+
+\bibitem{JSON:T. Bray Ed.}
+T. Bray, Ed., \emph{JSON}, \url{https://tools.ietf.org/html/rfc7159}, request for comment, accessed February 9th 2017
 
@@
 
-% that's all folks
 \end{document}

### 2017-02-12 paper.tex
Introduction, Implementation, component order, edit0r, disc0very

@@
 fl0w was developed out of a need for a fast, reliable and wireless workflow solution that can compete with the currently available offerings like Harrogate\cite{Harrogate:KIPR}.
-Its goals are to transform the connected controllers to a redundant fleet of logical units that share the same binaries and source code, real-time in-line sensor readouts, and a management layer inside the text editor as well as a browser-based interface.
+Its goals are to transform the connected controllers into a redundant fleet of logical units that share the same binaries and source code, programming, real-time in-line sensor readouts, and robot management inside Sublime Text 3\cite{Sublime Text 3:Sublime HQ}, and a browser-based front-end.
 
@@
 All fl0w components are designed as libraries to allow for integration into other projects.
+fl0w utilities a client-server networking model with random server assignment.
 
 \section{Components}
+\subsection{behem0th}
+
 \subsection{undergr0und}
-undergr0und\cite{undergr0und:Philip Trauner} is an asynchronous route based and data type preserving network protocol with peer-to-peer piping capabilities. 
+undergr0und\cite{undergr0und:Philip Trauner} is an asynchronous, route based, largely programming language agnostic, and data type preserving network protocol with peer-to-peer piping capabilities. 
 It automatically converts data into a transferable format and prepends binary headers to allow for reconstruction on the other end.
@@
 Before any communication takes place these lookup tables are exchanged.
-Route ID 0 is reserved by undergr0und\cite{undergr0und:Philip Trauner} for self management purposes.
+Route ID 0 is reserved for self management purposes.
 
@@
 There is no predefined mechanism in the network protocol that exposed these peer IDs, the application using undergr0und\cite{undergr0und:Philip Trauner} has to provide a way of making them available.
+This approach allows for more flexibility if additional host-metadata has to be provided.
 Pipe messages are packaged inside regular route messages with additional headers in the data segment.
 An optional server route called {\color{deepgreen}"pipe"} unpacks the regular and the extended headers and forwards the message to the targeted peer.
+The original sender ID is always included for a possible response.
+
+\subsection{dashb0ard}
+
+\subsection{edit0r}
+edit0r is the Sublime Text 3 plugin.
+It is modeled as a fl0w client and allows for remote robot management, source code synchronization as well as in line sensor readouts.
+It also provides quick access to dashb0ard, which is convenient because the IP addresses of controllers aren't necessarily static.
+behem0th\cite{behem0th:Christoph Heiss} is embedded into edit0r and enables the source code synchronization.
+
+\subsubsection{Robot selection}
+
+\subsubsection{Robot management}
+Botball programs can be started (keyboard shortcut: F8) and/or stopped (keyboard shortcut: F9). An identification sound can be invoked and the hostname of a controller can be set.
+
+\subsubsection{In-line sensor readouts}
+Invocations of the functions "analog" and "digital" are located every time the content of a view has changed and all required sensor ports are transmitted to the currently selected controller.
+The controller keeps track of all subscriptions to sensors and transmits the appropriate values to the Sublime Text\cite{Sublime Text 3:Sublime HQ} plugin.
+In-line sensor readouts can be toggled on a per view basis with a keyboard shortcut (default F10).
+
+\subsection{disc0very}
+fl0w is using a traditional client-server networking model but because of it's distributed nature the server is chosen randomly.
+This is implemented with UDP broadcasts that coordinate which controllers become clients and which controller becomes the server.
+
+\subsection{r0adrunner}
 
@@
 
+\bibitem{behem0th:Christoph Heiss}
+Christoph Heiss, \emph{behem0th}, \url{https://github.com/robot0nfire/behem0th}, source code, accessed February 9th 2017
+
 \bibitem{undergr0und:Philip Trauner}

### 2017-02-18 paper.tex
Added @Sybee as author, added paragraph about dashb0ard and edit0r
Improved Introduction and many parts of edit0r

@@
 HTBLuVA Wiener Neustadt\\
-Email: me@christoph-heiss.me}}
+Email: me@christoph-heiss.me}
+\and
+\IEEEauthorblockN{Sebastian Schaffler}
+\IEEEauthorblockA{School of Computer Engineering\\
+HTBLuVA Wiener Neustadt\\
+Email: se.schaffler@gmail.com}}
 
@@
 fl0w was developed out of a need for a fast, reliable and wireless workflow solution that can compete with the currently available offerings like Harrogate\cite{Harrogate:KIPR}.
-Its goals are to transform the connected controllers into a redundant fleet of logical units that share the same binaries and source code, programming, real-time in-line sensor readouts, and robot management inside Sublime Text 3\cite{Sublime Text 3:Sublime HQ}, and a browser-based front-end.
+Its goals are to transform the connected controllers into a redundant fleet of logical units that share the same binaries and source code, programming, real-time in-line sensor readouts, and robot management inside Sublime Text 3\cite{Sublime Text 3:Sublime HQ}, a browser-based front-end and the ability to connect to a wireless access point from withing a grahical user interface.
 
@@
 Python was chosen as the implementation language for fl0w because of its rich standard library and its lightweight virtual machine that can run on a Wallaby controller with acceptable speed.
-A pre-compiled version of Python 3.3.6 \cite{Python 3.3.6:Python Foundation} is bundled with the fl0w installer because it is not present on the Wallaby by default.
+A pre-compiled version of Python \cite{Python 3.3.6:Python Foundation} is bundled with the fl0w installer because it is not present on the Wallaby by default.
 All fl0w components are designed as libraries to allow for integration into other projects.
@@
 The Python\cite{Python 3.3.6:Python Foundation} version is built on top of a fork of ws4py\cite{ws4py:Philip Trauner} and the JavaScript version utilizes regular WebSockets\cite{The WebSocket Protocol:A.
-Melnikov} (in arraybuffer mode).
+Melnikov} in arraybuffer mode.
 It was created to mitigate the problems fl0ws explorative development style created.
-Instead of one monolithic network protocol, undergr0und consists of many small sub protocols.
+Instead of one monolithic network protocol, undergr0und emphasizes small sub protocols.
 This was done because all monolithic designs became too inconsistent.
@@
 \subsubsection{Exchange table}
-To reduce the required additional bandwidth per message that is introduced with variable character count routes a numbered route lookup table is generated on startup by clients and the server.
+To reduce the required additional bandwidth per message that is introduced with variable character count routes, a numbered route lookup table is generated on startup by clients and the server.
 Before any communication takes place these lookup tables are exchanged.
@@
 There is no predefined mechanism in the network protocol that exposed these peer IDs, the application using undergr0und\cite{undergr0und:Philip Trauner} has to provide a way of making them available.
-This approach allows for more flexibility if additional host-metadata has to be provided.
+This approach allows for more flexibility if additional peer-metadata has to be provided.
 Pipe messages are packaged inside regular route messages with additional headers in the data segment.
-An optional server route called {\color{deepgreen}"pipe"} unpacks the regular and the extended headers and forwards the message to the targeted peer.
+A server route called {\color{deepgreen}"pipe"} unpacks the regular and the extended headers and forwards the message to the targeted peer.
 The original sender ID is always included for a possible response.
@@
 \subsection{dashb0ard}
+dashb0ard is a single-page web front-end designed to manage the fl0w fleet.
+It can be used to configure every connected controller and obtain information from them.
+It utilises the JavaScript version of undergr0und to retrieve data from fl0w, Flot\cite{Flot:David Schnur} to display graphs and jQuery\cite{jQuery:jQuery Foundation} for DOM manipulation.
+
+\subsubsection{Sensor readouts}
 
@@
 It is modeled as a fl0w client and allows for remote robot management, source code synchronization as well as in line sensor readouts.
-It also provides quick access to dashb0ard, which is convenient because the IP addresses of controllers aren't necessarily static.
+It also provides quick access to dashb0ard, which is required because the IP addresses of controllers are not always static.
 behem0th\cite{behem0th:Christoph Heiss} is embedded into edit0r and enables the source code synchronization.
@@
 \subsection{r0adrunner}
+r0adrunner is the installer of fl0w.
+
+\subsection{fl0w}
+fl0w itself is the combination of all other components. Server and Wallaby client are the central pieces that make up fl0w.
 
 \section{Conclusion}
-The conclusion goes here.
 
@@
 
+\bibitem{bottle.py:Marcel Hellkamp}
+Marcel Hellkamp, \emph{bottle.py}, \url{https://github.com/bottlepy/bottle}, source code, accessed February 9th 2017
+
+\bibitem{Flot:David Schnur}
+David Schnur, \emph{Flot}, \url{https://github.com/flot/flot}, source code, accessed February 9th 2017
+
+\bibitem{jQuery:jQuery Foundation}
+jQuery Foundation, \emph{jQuery}, \url{https://jquery.com/}, product page, accessed February 9th 2017
+
 \end{thebibliography}

### 2017-02-24 paper.tex
Inluded microtype, enhanced behem0th and dashb0ard section, reorganization

@@
 \usepackage{cite}
+\usepackage{microtype}
 
@@
 fl0w was developed out of a need for a fast, reliable and wireless workflow solution that can compete with the currently available offerings like Harrogate\cite{Harrogate:KIPR}.
-Its goals are to transform the connected controllers into a redundant fleet of logical units that share the same binaries and source code, programming, real-time in-line sensor readouts, and robot management inside Sublime Text 3\cite{Sublime Text 3:Sublime HQ}, a browser-based front-end and the ability to connect to a wireless access point from withing a grahical user interface.
+Its goals are to transform the connected controllers into a redundant fleet of logical units that share the same binaries and source code, real-time in-line sensor readouts, programming as well as robot management inside Sublime Text 3\cite{Sublime Text 3:Sublime HQ}, a browser-based front-end and the ability to connect to a wireless access point.
 
@@
 Python was chosen as the implementation language for fl0w because of its rich standard library and its lightweight virtual machine that can run on a Wallaby controller with acceptable speed.
-A pre-compiled version of Python \cite{Python 3.3.6:Python Foundation} is bundled with the fl0w installer because it is not present on the Wallaby by default.
+A pre-compiled version of Python \cite{Python 3.3.6:Python Foundation} is bundled with the fl0w installer, r0adrunner, because it is not present on the Wallaby by default.
 All fl0w components are designed as libraries to allow for integration into other projects.
@@
 \section{Components}
-\subsection{behem0th}
 
@@
 
+\subsection{behem0th}
+behem0th is a continuous network file synchronization protocol developed out of the need for an embeddable solution that would not require an additional background program to be present on the system running Sublime Text 3\cite{Sublime Text 3:Sublime HQ}, instead utilizing its plugin environment.
+It uses a client-server networking model without peer-to-peer capabilities to stay in line with undergr0und.
+
+\subsubsection{Synchronization}
+Files are synchronized based on modification time and md5 hash. Sync conflicts are resolved on the server.
+
+\subsubsection{Transfer}
+behem0th neither sends nor receives files as a whole, instead it transmits the file size followed by data block which are written to a temporary file on disk.
+This is done to allow the transfer of files that are large enough to cause out of system memory situations.
+
 \subsection{dashb0ard}
 dashb0ard is a single-page web front-end designed to manage the fl0w fleet.
-It can be used to configure every connected controller and obtain information from them.
-It utilises the JavaScript version of undergr0und to retrieve data from fl0w, Flot\cite{Flot:David Schnur} to display graphs and jQuery\cite{jQuery:jQuery Foundation} for DOM manipulation.
+It can be used to configure connected controllers and obtain information from them.
+It utilities the JavaScript version of undergr0und to retrieve data from fl0w, Flot\cite{Flot:David Schnur} to display graphs and jQuery\cite{jQuery:jQuery Foundation} for DOM manipulation.
 
@@
 \subsection{disc0very}
-fl0w is using a traditional client-server networking model but because of it's distributed nature the server is chosen randomly.
+fl0w is using a client-server networking model but because of it's distributed nature the server is chosen randomly.
 This is implemented with UDP broadcasts that coordinate which controllers become clients and which controller becomes the server.

### 2017-03-03 paper.tex
Reworked undergr0und section

@@
 Melnikov} in arraybuffer mode.
-It was created to mitigate the problems fl0ws explorative development style created.
+Only the Python version can be started in server mode because It was created to mitigate the problems fl0ws explorative development style created.
 Instead of one monolithic network protocol, undergr0und emphasizes small sub protocols.
@@
 undergr0und\cite{undergr0und:Philip Trauner} manages itself through its own concepts.
+
+\subsubsection{undergr0und.js}
+undergr0und.js is the feature complete client-side JavaScript port of undergr0und.
+It utilizes node-jspack to unpack the binary messages it receives from the undergr0und server.
+It is based on the Python version.
 

### 2017-03-11 paper.tex
Improved: undergr0und.js, route, behem0th, citations, edit0r

@@
 It utilizes node-jspack to unpack the binary messages it receives from the undergr0und server.
-It is based on the Python version.
+It is based on the Python version but does not implement the server because there is currently no need for that functionality.
 
@@
 \subsubsection{Route}
-A client$\,\to\,$server / server$\,\to\,$client construct.
+A client$\,\to\,$server / server$\,\to\,$client construct. Invoked with the {\color{deepgreen}"send"} call.
 
@@
 A client$\,\to\,$server$\,\to\,$client construct.
+Invoked with the {\color{deepgreen}"pipe"} call.
 Clients can be targeted with unique IDs that are generated randomly for all connected peers by the server.
@@
 It uses a client-server networking model without peer-to-peer capabilities to stay in line with undergr0und.
+It uses regular sockets instead of WebSockets\cite{The WebSocket Protocol:A.
+Melnikov} because the in-browser components of fl0w never interact with it.
+File system events are detected with watchdog
 
@@
 This is done to allow the transfer of files that are large enough to cause out of system memory situations.
+
+\subsubsection{Metadata}
+Metadata
 
@@
 \subsubsection{Robot selection}
+fl0ws networking model allows for the management of multiple controllers without a direct connection to them.
+The controller hostname is utilised to identify the robots in the user-interface.
+Controllers can be selected to obtain additional functionality such as in-line sensor readouts and keyboard shortcuts.
 
 \subsubsection{Robot management}
-Botball programs can be started (keyboard shortcut: F8) and/or stopped (keyboard shortcut: F9). An identification sound can be invoked and the hostname of a controller can be set.
+Botball programs can be started (keyboard shortcut: F8) and/or stopped (keyboard shortcut: F9).
+Additionally, edit0r allows for modification of the controller hostname, playback of a sound for identification purposes, listing of running processes, power management functionality (reboot, shutdown) and running programs.
 
 \subsubsection{In-line sensor readouts}
-Invocations of the functions "analog" and "digital" are located every time the content of a view has changed and all required sensor ports are transmitted to the currently selected controller.
-The controller keeps track of all subscriptions to sensors and transmits the appropriate values to the Sublime Text\cite{Sublime Text 3:Sublime HQ} plugin.
+Invocations of the functions "analog" and "digital" are located every time the content of a view changes and the parameters of the calls are grouped across views.
+edit0r subscribes to all required sensor ports by requesting them from the currently selected controller.
+The controller keeps track of all subscriptions to sensors and continuously transmits the appropriate values to the Sublime Text\cite{Sublime Text 3:Sublime HQ} plugin.
+Sublime Text \cite{Sublime Text 3:Sublime HQ} phantoms are created as soon as new sensor values are available.
+This approach has the disadvantage of higher than usual processor utilization by edit0r, because phantoms were primarily designed to display infrequently updated content.
+To partially circumvent this, sensor readouts can be disabled as well.\\
 In-line sensor readouts can be toggled on a per view basis with a keyboard shortcut (default F10).
@@
 \subsection{fl0w}
-fl0w itself is the combination of all other components. Server and Wallaby client are the central pieces that make up fl0w.
+fl0w itself is the combination of all other components split into Wallaby client and server.
+
+\subsubsection{Wallaby}
 
@@
 \bibitem{Python 3.3.6:Python Foundation}
-Python Foundation, \emph{Python 3.3.6}, \url{https://www.python.org/downloads/release/python-336/}, source code, accessed February 9th 2017
+Python Foundation, \emph{Python 3.3.6}, \url{https://www.python.org/downloads/release/python-336/},\\ source code,
+accessed February 9th 2017
 
 \bibitem{behem0th:Christoph Heiss}
-Christoph Heiss, \emph{behem0th}, \url{https://github.com/robot0nfire/behem0th}, source code, accessed February 9th 2017
+Christoph Heiss, \emph{behem0th}, \url{https://github.com/robot0nfire/behem0th},\\ source code,
+accessed February 9th 2017
 
 \bibitem{undergr0und:Philip Trauner}
-Philip Trauner, \emph{undergr0und}, \url{https://github.com/robot0nfire/fl0w/wiki/undergr0und}, implementation notes, accessed February 9th 2017
+Philip Trauner, \emph{undergr0und}, \url{https://github.com/robot0nfire/fl0w/wiki/undergr0und},\\ implementation notes,
+accessed February 9th 2017
 
 \bibitem{ws4py:Philip Trauner}
-Philip Trauner, \emph{ws4py}, \url{https://github.com/robot0nfire/ws4py}, source code, accessed February 9th 2017
+Philip Trauner, \emph{ws4py}, \url{https://github.com/robot0nfire/ws4py},\\ source code,
+accessed February 9th 2017
 
 \bibitem{The WebSocket Protocol:A. Melnikov}
-A. Melnikov, \emph{The WebSocket Protocol}, \url{https://tools.ietf.org/html/rfc6455}, request for comment, accessed February 9th 2017
+A. Melnikov, \emph{The WebSocket Protocol}, \url{https://tools.ietf.org/html/rfc6455},\\ request for comment,
+accessed February 9th 2017
+
+\bibitem{watchdog:Yesudeep Mangalapilly}
+Yesudeep Mangalapilly, \emph{watchdog}, \url{https://github.com/gorakhargosh/watchdog},\\ source code,
+accessed February 9th 2017
 
 \bibitem{JSON:T. Bray Ed.}
-T. Bray, Ed., \emph{JSON}, \url{https://tools.ietf.org/html/rfc7159}, request for comment, accessed February 9th 2017
+T. Bray, Ed., \emph{JSON}, \url{https://tools.ietf.org/html/rfc7159},\\ request for comment,
+accessed February 9th 2017
 
 \bibitem{bottle.py:Marcel Hellkamp}
-Marcel Hellkamp, \emph{bottle.py}, \url{https://github.com/bottlepy/bottle}, source code, accessed February 9th 2017
+Marcel Hellkamp, \emph{bottle.py}, \url{https://github.com/bottlepy/bottle},\\ source code,
+accessed February 9th 2017
 
 \bibitem{Flot:David Schnur}
-David Schnur, \emph{Flot}, \url{https://github.com/flot/flot}, source code, accessed February 9th 2017
+David Schnur, \emph{Flot}, \url{https://github.com/flot/flot},\\ source code,
+accessed February 9th 2017
 
 \bibitem{jQuery:jQuery Foundation}
-jQuery Foundation, \emph{jQuery}, \url{https://jquery.com/}, product page, accessed February 9th 2017
+jQuery Foundation, \emph{jQuery}, \url{https://jquery.com/},\\ product page,
+accessed February 9th 2017
 

### 2017-03-12 paper.tex
Improved: undergr0und.js, behem0th, fl0w server

@@
 Melnikov} in arraybuffer mode.
-Only the Python version can be started in server mode because It was created to mitigate the problems fl0ws explorative development style created.
+It was created to mitigate the problems fl0ws explorative development style created.
 Instead of one monolithic network protocol, undergr0und emphasizes small sub protocols.
-This was done because all monolithic designs became too inconsistent.
+This was done because all monolithic designs became too inconsistent over time.
 undergr0und\cite{undergr0und:Philip Trauner} manages itself through its own concepts.
@@
 \subsubsection{undergr0und.js}
-undergr0und.js is the feature complete client-side JavaScript port of undergr0und.
+undergr0und.js is the feature complete client-side JavaScript port of undergr0und that was required for dashb0ard, the browser-based front-end for fl0w.
 It utilizes node-jspack to unpack the binary messages it receives from the undergr0und server.
 It is based on the Python version but does not implement the server because there is currently no need for that functionality.
+undergr0und.js can run be used in Node.js\cite{Node.js:Node.js Foundation} as well as browsers that support WebSockets\cite{The WebSocket Protocol:A.
+Melnikov}.
+browserify\cite{browserify:James Halliday} is used to create the browser version.
 
@@
 Melnikov} because the in-browser components of fl0w never interact with it.
-File system events are detected with watchdog
+File system events are detected with watchdog\cite{watchdog:Yesudeep Mangalapilly}.
 
 \subsubsection{Synchronization}
-Files are synchronized based on modification time and md5 hash. Sync conflicts are resolved on the server.
+Files are synchronized based on modification time and md5 hash. Sync conflicts are resolved on the server. Synchronization with a theoretically indefinite amount of clients is possible.
 
@@
 
-\subsubsection{Metadata}
-Metadata
-
 \subsection{dashb0ard}
 dashb0ard is a single-page web front-end designed to manage the fl0w fleet.
-It can be used to configure connected controllers and obtain information from them.
-It utilities the JavaScript version of undergr0und to retrieve data from fl0w, Flot\cite{Flot:David Schnur} to display graphs and jQuery\cite{jQuery:jQuery Foundation} for DOM manipulation.
+It can be used to configure connected controllers and obtain sensor readouts as well as debug logs.
+It utilities the JavaScript version of undergr0und to retrieve data from fl0w, Vue.js for its user interface, Charts.js to display graphs and jQuery\cite{jQuery:jQuery Foundation} for additional DOM manipulation.
 
@@
 edit0r is the Sublime Text 3 plugin.
-It is modeled as a fl0w client and allows for remote robot management, source code synchronization as well as in line sensor readouts.
+It is modeled as a fl0w client and allows for remote robot management, source code synchronization as well as in-line sensor readouts.
 It also provides quick access to dashb0ard, which is required because the IP addresses of controllers are not always static.
@@
 
-\subsubsection{Wallaby}
+\subsubsection{Wallaby client}
+
+\subsubsection{Server}
+The server keeps track of all clients and provides means to acquire their peer IDs, which are used by undergr0und to target specific clients.
+Additionally it serves dashb0ard and handles program compilation.
+It utilizes undergr0und for networking, behem0th for file-synchronization, and disc0very to determine if another server is already running in the network.
+In that case the start is interrupted and the Wallaby client connects to the available server instance, otherwise server and client are started.
 
@@
 
+\bibitem{browserify:James Halliday}
+James Halliday, \emph{browserify}, \url{http://browserify.org/},\\ product page,
+accessed February 9th 2017
+
+\bibitem{Node.js:Node.js Foundation}
+Node.js Foundation, \emph{Node.js}, \url{https://nodejs.org},\\ product page,
+accessed February 9th 2017
+
+\bibitem{watchdog:Yesudeep Mangalapilly}
+Yesudeep Mangalapilly, \emph{watchdog}, \url{https://github.com/gorakhargosh/watchdog}, \\ source code, accessed February 9th 2017
+
 \end{thebibliography}

### 2017-03-14 paper.tex
Added conclusion, improved behem0th, r0adrunner

@@
 This was done because all monolithic designs became too inconsistent over time.
-undergr0und\cite{undergr0und:Philip Trauner} manages itself through its own concepts.
+undergr0und\cite{undergr0und:Philip Trauner} manages itself through its own concepts.\\
 
@@
 Melnikov}.
-browserify\cite{browserify:James Halliday} is used to create the browser version.
+browserify\cite{browserify:James Halliday} is used to create the browser version.\\
 
@@
 Before any communication takes place these lookup tables are exchanged.
-Route ID 0 is reserved for self management purposes.
+Route ID 0 is reserved for self management purposes.\\
 
@@
 
-\subsubsection{Data type preservation}
-The original type of the data segment is present inside the header $($see Figure ~\ref{fig:undergr0und_header}$)$ to accurately reconstruct sent data on the other end.
-JSON\cite{JSON:T.
-Bray Ed.} is used to transfer lists and dictionaries, and regular ASCII encoded strings are utilized to transfer integers, floats, null/none types and strings.
-
 \subsubsection{Route}
-A client$\,\to\,$server / server$\,\to\,$client construct. Invoked with the {\color{deepgreen}"send"} call.
+A client$\,\to\,$server / server$\,\to\,$client construct. Invoked with the {\color{deepgreen}"send"} call. \newpage
 
@@
 A server route called {\color{deepgreen}"pipe"} unpacks the regular and the extended headers and forwards the message to the targeted peer.
-The original sender ID is always included for a possible response.
+The original sender ID is always included for a possible response.\\
+
+\subsubsection{Data type preservation}
+The original type of the data segment is present inside the header $($see Figure ~\ref{fig:undergr0und_header}$)$ to accurately reconstruct sent data on the other end.
+JSON\cite{JSON:T.
+Bray Ed.} is used to transfer lists and dictionaries, and regular ASCII encoded strings are utilized to transfer integers, floats, null/none types and strings.
 
@@
 File system events are detected with watchdog\cite{watchdog:Yesudeep Mangalapilly}.
+\\
 
 \subsubsection{Synchronization}
-Files are synchronized based on modification time and md5 hash. Sync conflicts are resolved on the server. Synchronization with a theoretically indefinite amount of clients is possible.
+Files are synchronized based on modification time and md5 hash. Sync conflicts are resolved on the server. Synchronization with a theoretically indefinite amount of clients is possible.\\
 
@@
 behem0th neither sends nor receives files as a whole, instead it transmits the file size followed by data block which are written to a temporary file on disk.
-This is done to allow the transfer of files that are large enough to cause out of system memory situations.
+This is done to allow the transfer of files that are large enough to cause out of system memory situations.\\
+
+\subsubsection{Protocol}
+behem0th is independent from underg0und and defines its own network protocol.
+It also utilizes different routes nonetheless, which are directly perpended to the data segment, for file list transmission as well as actual date transfers.
+
+\begin{figure}[H]
+\centering
+	\begin{tabular}{*{2}{V}}
+		Data size & (Route) Data \\ \hline
+		4 & * \\
+	\end{tabular}
+	\caption{The binary encoding of behem0th (in bytes)}
+\label{fig:behem0th_header}
+\end{figure}
 
@@
 It can be used to configure connected controllers and obtain sensor readouts as well as debug logs.
-It utilities the JavaScript version of undergr0und to retrieve data from fl0w, Vue.js for its user interface, Charts.js to display graphs and jQuery\cite{jQuery:jQuery Foundation} for additional DOM manipulation.
+It utilities the JavaScript version of undergr0und to retrieve data from fl0w, Vue.js for its user interface, Bootstrap 3 as a design baseline, Charts.js to display graphs and jQuery\cite{jQuery:jQuery Foundation} for additional DOM manipulation.
 
@@
 It is modeled as a fl0w client and allows for remote robot management, source code synchronization as well as in-line sensor readouts.
-It also provides quick access to dashb0ard, which is required because the IP addresses of controllers are not always static.
+\\It also provides quick access to dashb0ard, which is required because the IP addresses of controllers are not always static.
 behem0th\cite{behem0th:Christoph Heiss} is embedded into edit0r and enables the source code synchronization.
+In its current form only C programs are supported.\\
 
@@
 The controller hostname is utilised to identify the robots in the user-interface.
-Controllers can be selected to obtain additional functionality such as in-line sensor readouts and keyboard shortcuts.
+Controllers can be selected to obtain additional functionality such as in-line sensor readouts and keyboard shortcuts.\\
 
@@
 Botball programs can be started (keyboard shortcut: F8) and/or stopped (keyboard shortcut: F9).
-Additionally, edit0r allows for modification of the controller hostname, playback of a sound for identification purposes, listing of running processes, power management functionality (reboot, shutdown) and running programs.
+Additionally, edit0r allows for modification of the controller hostname, playback of a sound for identification purposes, listing of running processes, power management functionality (reboot, shutdown) and running programs.\\
 
@@
 The controller keeps track of all subscriptions to sensors and continuously transmits the appropriate values to the Sublime Text\cite{Sublime Text 3:Sublime HQ} plugin.
-Sublime Text \cite{Sublime Text 3:Sublime HQ} phantoms are created as soon as new sensor values are available.
+\\Sublime Text \cite{Sublime Text 3:Sublime HQ} phantoms are created as soon as new sensor values are available.
 This approach has the disadvantage of higher than usual processor utilization by edit0r, because phantoms were primarily designed to display infrequently updated content.
-To partially circumvent this, sensor readouts can be disabled as well.\\
-In-line sensor readouts can be toggled on a per view basis with a keyboard shortcut (default F10).
+To partially circumvent this, sensor readouts can be disabled and are not enabled by default.\\
+In-line sensor readouts can be toggled on a per view basis with a keyboard shortcut (default F10).\\
 
@@
 r0adrunner is the installer of fl0w.
+It is built to mimic a Wallaby controller software update to remain compatible with the preexisting update functionality found in Harrogate.
+It is implemented in Python 2.7, which is already installed on all Wallaby controllers but because fl0w utilizes features of Python 3.3 it installs a full-fledged precompiled version of Python 3.6.0.
+It also changes the Wallaby hostname to their unique manufacturing ID because fl0w utilizes hostnames to represent controllers in its user facing components.
+r0adrunner is distributed as an archive that has to be copied to an USB storage medium.
 
 \subsection{fl0w}
-fl0w itself is the combination of all other components split into Wallaby client and server.
+fl0w itself is the combination of all other components split into Wallaby client and server.\\
 
 \subsubsection{Wallaby client}
+The Wallaby client serves as an information source for sensor values, program output, as well as currently running processes. Additionally it exposes its own standard output for monitoring purposes.\\
 
@@
 It utilizes undergr0und for networking, behem0th for file-synchronization, and disc0very to determine if another server is already running in the network.
-In that case the start is interrupted and the Wallaby client connects to the available server instance, otherwise server and client are started.
+In that situation the start is interrupted, the Wallaby client is started and it connects to the available server instance, otherwise server and client are started.
+\\
 
 \section{Conclusion}
+
+After prolonged testing it was deemed reasonable to claim that fl0w can improve the robotics development work-flow on Wallaby controllers.
+
+Networking boilerplate code can be cut down drastically with a fitting networking solution already in place.
+
+Security was never a design goal, instead relying on network interface level security was chosen to save time. This assumption will cause problems in densely populated wireless networks.
+
+Support for Python as a robot programming language as well as basic remote procedure call functionality is the next development goal.
 

### 2017-03-16 paper.tex
Add some more text about behem0th

@@
 It uses regular sockets instead of WebSockets\cite{The WebSocket Protocol:A.
-Melnikov} because the in-browser components of fl0w never interact with it.
-File system events are detected with watchdog\cite{watchdog:Yesudeep Mangalapilly}.
-\\
+Melnikov} because the in-browser components of fl0w never interacts with it.
+The file-system is monitored using the watchdog\cite{watchdog:Yesudeep Mangalapilly} library.\\
 
 \subsubsection{Synchronization}
-Files are synchronized based on modification time and md5 hash. Sync conflicts are resolved on the server. Synchronization with a theoretically indefinite amount of clients is possible.\\
+On startup, behem0th synchronizes files based on their last modification time and MD5 hash.
+After that, files get synchronized to other clients as soon as a file-system event happens.
+Synchronization conflicts are resolved on the server and it is possible to use behem0th with a theoretically indefinite amount of clients.\\
 
@@
 behem0th is independent from underg0und and defines its own network protocol.
-It also utilizes different routes nonetheless, which are directly perpended to the data segment, for file list transmission as well as actual date transfers.
+It also utilizes different routes nonetheless, which are directly perpended to the data segment, for file list transmission as well as actual date transfers.\\
+
+\subsubsection{Security}
+Although MD5 is deprecated and known to suffers from extensive vulnerabilities, behem0th is designed to only run in a local network, which is controlled by the users of fl0w.
+This assumption also simplifies the implementation greatly.\\
 

### 2017-03-16 paper.tex
Add reference to Boostrap 3

@@
 It can be used to configure connected controllers and obtain sensor readouts as well as debug logs.
-It utilities the JavaScript version of undergr0und to retrieve data from fl0w, Vue.js for its user interface, Bootstrap 3 as a design baseline, Charts.js to display graphs and jQuery\cite{jQuery:jQuery Foundation} for additional DOM manipulation.
+It utilities the JavaScript version of undergr0und to retrieve data from fl0w, Vue.js for its user interface, Bootstrap 3\cite{Bootstrap 3:Twitter Inc.} as a design baseline, Charts.js to display graphs and jQuery\cite{jQuery:jQuery Foundation} for additional DOM manipulation.
 
@@
 
-\bibitem{watchdog:Yesudeep Mangalapilly}
-Yesudeep Mangalapilly, \emph{watchdog}, \url{https://github.com/gorakhargosh/watchdog}, \\ source code, accessed February 9th 2017
+\bibitem{Bootstrap 3:Twitter Inc.}
+Twitter, Inc., \emph{Bootstrap 3}, \url{http://getbootstrap.com},\\ product page,
+accessed March 16th 2017
 

### 2017-03-22 paper.tex
Update behem0ths protocol description.

@@
 \pythonstyle
+\lstset{#1}
+}
+{}
+
+% Define JSON language
+\lstdefinelanguage{json}
+{
+morestring=[b]" % defines that strings are enclosed in double quotes
+}
+
+% JSON style for highlighting
+\newcommand\jsonstyle{\lstset{
+language=json,
+basicstyle=\ttm,
+stringstyle=\color{deepgreen},
+frame=tb,
+showstringspaces=false
+}}
+
+% JSON environment
+\lstnewenvironment{json}[1][]
+{
+\jsonstyle
 \lstset{#1}
@@
 \subsubsection{Transfer}
-behem0th neither sends nor receives files as a whole, instead it transmits the file size followed by data block which are written to a temporary file on disk.
-This is done to allow the transfer of files that are large enough to cause out of system memory situations.\\
+behem0th neither sends nor receives files as a whole, instead it transmits the file as small blocks (4096 bytes), which are written to a temporary file on disk as soon as they are received.
+This is done to allow the transfer of large files even in very memory-constrained environments.\\
 
@@
 behem0th is independent from underg0und and defines its own network protocol.
-It also utilizes different routes nonetheless, which are directly perpended to the data segment, for file list transmission as well as actual date transfers.\\
+It is completely text-based, uses UTF-8\cite{UTF-8:F.
+Yergeau} for character encoding and JSON\cite{JSON:T.
+Bray Ed.} as format encoding.
+behem0th is designed around 'requests' $($see Figure ~\ref{fig:behem0th_request}$)$ and 'routes'.
+Each request is a JSON-formatted string and separated by a newline.
+
+\begin{figure}[H]
+\centering
+\begin{json}
+{
+    "route": "<route-name>",
+    "data": "<route-specific data>"
+}
+\end{json}
+\caption{behem0th request}
+\label{fig:behem0th_request}
+\end{figure}
+
+A route can also send additional data if needed (a 'payload').
+For binary data, base64\cite{Base64:S.
+Josefsson} encoding is used.
+After the payload, there is again a newline to delimit payload and the next request.
+\\
 
@@
 This assumption also simplifies the implementation greatly.\\
-
-\begin{figure}[H]
-\centering
-	\begin{tabular}{*{2}{V}}
-		Data size & (Route) Data \\ \hline
-		4 & * \\
-	\end{tabular}
-	\caption{The binary encoding of behem0th (in bytes)}
-\label{fig:behem0th_header}
-\end{figure}
 
@@
 
+\bibitem{UTF-8:F. Yergeau}
+F. Yergeau, \emph{UTF-8}, \url{https://tools.ietf.org/html/rfc3629},\\ request for comment,
+accessed March 22nd 2017
+
 \bibitem{JSON:T. Bray Ed.}
@@
 accessed February 9th 2017
+
+\bibitem{Base64:S. Josefsson}
+S. Josefsson, \emph{Base64}, \url{https://tools.ietf.org/html/rfc4648}, \\ request for comment,
+accessed March 22nd 2017
 

### 2017-03-22 paper.tex
Removed: disc0very; Added: References; General: Cleanup

@@
 \title{fl0w 2.0 - a development environment for the\\ KIPR Wallaby}
-\author{\IEEEauthorblockN{Philip Trauner}
-\IEEEauthorblockA{School of Computer Engineering\\
-HTBLuVA Wiener Neustadt\\
-Email: philip.trauner@arztpraxis.io}
-\and
-\IEEEauthorblockN{Christoph Heiss}
-\IEEEauthorblockA{School of Computer Engineering\\
-HTBLuVA Wiener Neustadt\\
-Email: me@christoph-heiss.me}
-\and
-\IEEEauthorblockN{Sebastian Schaffler}
-\IEEEauthorblockA{School of Computer Engineering\\
-HTBLuVA Wiener Neustadt\\
-Email: se.schaffler@gmail.com}}
-
+\author{\IEEEauthorblockN{Philip Trauner, Christoph Heiss, Sebastian Schaffler, Nico Kratky, Nico Leidenfrost, Christine Zeh, Sascha Zemann}
+\IEEEauthorblockA{Department for Computer Science\\
+Secondary Technical College\\
+Wiener Neustadt, Austria\\
+Email: philip.trauner@arztpraxis.io, me@christoph-heiss.me, se.schaffler@gmail.com, \\nico@nicokratky.me, leidenfrost.nico@gmail.com, krixizeh@gmail.com, sascha.zemann@gmail.com}
+}
 \maketitle
@@
 \subsubsection{Route}
-A client$\,\to\,$server / server$\,\to\,$client construct. Invoked with the {\color{deepgreen}"send"} call. \newpage
+A client$\,\to\,$server / server$\,\to\,$client construct. Invoked with the {\color{deepgreen}"send"} call.
 
@@
 It can be used to configure connected controllers and obtain sensor readouts as well as debug logs.
-It utilities the JavaScript version of undergr0und to retrieve data from fl0w, Vue.js for its user interface, Bootstrap 3\cite{Bootstrap 3:Twitter Inc.} as a design baseline, Charts.js to display graphs and jQuery\cite{jQuery:jQuery Foundation} for additional DOM manipulation.
-
-\subsubsection{Sensor readouts}
+It utilities the JavaScript version of undergr0und to retrieve data from fl0w, Vue.js\cite{Vue:Evan You} for its user interface, Bootstrap 3\cite{Bootstrap 3:Twitter Inc.} as a design baseline, Flot\cite{Flot:David Schnur} to display graphs and jQuery\cite{jQuery:jQuery Foundation} for additional DOM manipulation.
 
@@
 In-line sensor readouts can be toggled on a per view basis with a keyboard shortcut (default F10).\\
-
-\subsection{disc0very}
-fl0w is using a client-server networking model but because of it's distributed nature the server is chosen randomly.
-This is implemented with UDP broadcasts that coordinate which controllers become clients and which controller becomes the server.
 
@@
 
+\bibitem{Vue:Evan You}
+Evan You, \emph{Vue.js}, \url{https://vuejs.org/},\\ product page,
+accessed March 16th 2017
+
 \end{thebibliography}

### 2017-03-30 paper.tex
Order references by first occurence
Images, improvements

@@
 \usepackage{microtype}
+\usepackage{graphicx}
+
+\graphicspath{ {images/} }
 
@@
 \begin{abstract}
-This publication introduces fl0w, an alternative\\ development environment for the KIPR Wallaby.\\ The aim of fl0w is to improve the robotics program development experience.
-It focuses on the components that make up fl0w, namely a file synchronization protocol that maintains a consistent state across all connected controllers, a route based and data type preserving network protocol with peer-to-peer piping capabilities, a discovery protocol that connects all controllers together automatically, a Sublime Text 3\cite{Sublime Text 3:Sublime HQ} plugin which enables in-line sensor readouts, program execution, program editing, and keyboard shortcuts, and a browser-based management front-end to manage the controller fleet.\\
+This publication introduces fl0w\cite{fl0w:Philip Trauner}, an alternative\\ development environment for the KIPR Wallaby\cite{Wallaby Controller:KIPR}.\\ The aim of fl0w\cite{fl0w:Philip Trauner} is to improve the robotics program development experience.
+It focuses on the components that make up fl0w\cite{fl0w:Philip Trauner}, namely a file synchronization protocol that maintains a consistent state across all connected controllers, a route based and data type preserving network protocol with peer-to-peer piping capabilities, a discovery protocol that connects all controllers together automatically, a Sublime Text 3\cite{Sublime Text 3:Sublime HQ} plugin which enables in-line sensor readouts, program execution, program editing, and keyboard shortcuts, and a browser-based management front-end to manage the controller fleet.\\
 \end{abstract}
@@
 \section{Introduction}
-fl0w was developed out of a need for a fast, reliable and wireless workflow solution that can compete with the currently available offerings like Harrogate\cite{Harrogate:KIPR}.
+fl0w\cite{fl0w:Philip Trauner} was developed out of a need for a fast, reliable and wireless workflow solution that can compete with the currently available offerings like Harrogate\cite{Harrogate:KIPR}.
 Its goals are to transform the connected controllers into a redundant fleet of logical units that share the same binaries and source code, real-time in-line sensor readouts, programming as well as robot management inside Sublime Text 3\cite{Sublime Text 3:Sublime HQ}, a browser-based front-end and the ability to connect to a wireless access point.
@@
 \section{Implementation}
-All fl0w components emphasize shared code and are therefor written in Python 3.3.6\cite{Python 3.3.6:Python Foundation} to remain compatible with the Sublime Text 3\cite{Sublime Text 3:Sublime HQ} plugin environment.
-Python was chosen as the implementation language for fl0w because of its rich standard library and its lightweight virtual machine that can run on a Wallaby controller with acceptable speed.
-A pre-compiled version of Python \cite{Python 3.3.6:Python Foundation} is bundled with the fl0w installer, r0adrunner, because it is not present on the Wallaby by default.
-All fl0w components are designed as libraries to allow for integration into other projects.
-fl0w utilities a client-server networking model with random server assignment.
+All fl0w\cite{fl0w:Philip Trauner} components emphasize shared code and are therefor written in Python\cite{Python:Python Foundation} 3.3.6 to remain compatible with the Sublime Text 3\cite{Sublime Text 3:Sublime HQ} plugin environment.
+Python\cite{Python:Python Foundation} was chosen as the implementation language for fl0w\cite{fl0w:Philip Trauner} because of its rich standard library and its lightweight virtual machine that can run on a Wallaby\cite{Wallaby Controller:KIPR} controller with acceptable speed.
+A pre-compiled version of Python\cite{Python:Python Foundation} is bundled with the fl0w\cite{fl0w:Philip Trauner} installer, r0adrunner, because it is not present on the Wallaby\cite{Wallaby Controller:KIPR} by default.
+All fl0w\cite{fl0w:Philip Trauner} components are designed as libraries to allow for integration into other projects.
+fl0w\cite{fl0w:Philip Trauner} utilities a client-server networking model with random server assignment.
 
@@
 
-\begin{figure}[H]
+\begin{table}[H]
+\caption{The binary encoding of undergr0und (in bytes)}
 \centering
@@
 	\end{tabular}
-	\caption{The binary encoding of undergr0und (in bytes)}
 \label{fig:undergr0und_header}
-\end{figure}
+\end{table}
 
-The Python\cite{Python 3.3.6:Python Foundation} version is built on top of a fork of ws4py\cite{ws4py:Philip Trauner} and the JavaScript version utilizes regular WebSockets\cite{The WebSocket Protocol:A.
+The Python\cite{Python:Python Foundation} version is built on top of a fork of ws4py\cite{ws4py:Philip Trauner} and the JavaScript version utilizes regular WebSockets\cite{The WebSocket Protocol:A.
 Melnikov} in arraybuffer mode.
-It was created to mitigate the problems fl0ws explorative development style created.
+It was created to mitigate the problems fl0ws\cite{fl0w:Philip Trauner}explorative development style created.
 Instead of one monolithic network protocol, undergr0und emphasizes small sub protocols.
@@
 \subsubsection{undergr0und.js}
-undergr0und.js is the feature complete client-side JavaScript port of undergr0und that was required for dashb0ard, the browser-based front-end for fl0w.
-It utilizes node-jspack to unpack the binary messages it receives from the undergr0und server.
-It is based on the Python version but does not implement the server because there is currently no need for that functionality.
+undergr0und.js\cite{undergr0und.js:Philip Trauner} is the feature complete client-side JavaScript port of undergr0und\cite{undergr0und:Philip Trauner} that was required for dashb0ard\cite{dashb0ard:Sebastian Schaffler}, the browser-based front-end for fl0w\cite{fl0w:Philip Trauner}.
+It utilizes node-jspack\cite{node-jspack:Peter Griess} to unpack the binary messages it receives from the undergr0und\cite{undergr0und:Philip Trauner} server.
+It is based on the Python\cite{Python:Python Foundation} version but does not implement the server because there is currently no need for that functionality.
 undergr0und.js can run be used in Node.js\cite{Node.js:Node.js Foundation} as well as browsers that support WebSockets\cite{The WebSocket Protocol:A.
@@
 \subsubsection{Data type preservation}
-The original type of the data segment is present inside the header $($see Figure ~\ref{fig:undergr0und_header}$)$ to accurately reconstruct sent data on the other end.
+The original type of the data segment is present inside the header $($see Table ~\ref{fig:undergr0und_header}$)$ to accurately reconstruct sent data on the other end.
 JSON\cite{JSON:T.
@@
 \subsection{behem0th}
-behem0th is a continuous network file synchronization protocol developed out of the need for an embeddable solution that would not require an additional background program to be present on the system running Sublime Text 3\cite{Sublime Text 3:Sublime HQ}, instead utilizing its plugin environment.
+behem0th\cite{behem0th:Christoph Heiss} is a continuous network file synchronization protocol developed out of the need for an embeddable solution that would not require an additional background program to be present on the system running Sublime Text 3\cite{Sublime Text 3:Sublime HQ}, instead utilizing its plugin environment.
 It uses a client-server networking model without peer-to-peer capabilities to stay in line with undergr0und.
 It uses regular sockets instead of WebSockets\cite{The WebSocket Protocol:A.
-Melnikov} because the in-browser components of fl0w never interacts with it.
+Melnikov} because the in-browser components of fl0w\cite{fl0w:Philip Trauner} never interacts with it.
 The file-system is monitored using the watchdog\cite{watchdog:Yesudeep Mangalapilly} library.\\
@@
 \subsubsection{Synchronization}
-On startup, behem0th synchronizes files based on their last modification time and MD5 hash.
+On startup, behem0th\cite{behem0th:Christoph Heiss} synchronizes files based on their last modification time and MD5 hash.
 After that, files get synchronized to other clients as soon as a file-system event happens.
-Synchronization conflicts are resolved on the server and it is possible to use behem0th with a theoretically indefinite amount of clients.\\
+Synchronization conflicts are resolved on the server and it is possible to use behem0th\cite{behem0th:Christoph Heiss} with a theoretically indefinite amount of clients.\\
 
 \subsubsection{Transfer}
-behem0th neither sends nor receives files as a whole, instead it transmits the file as small blocks (4096 bytes), which are written to a temporary file on disk as soon as they are received.
+behem0th\cite{behem0th:Christoph Heiss} neither sends nor receives files as a whole, instead it transmits the file as small blocks (4096 bytes), which are written to a temporary file on disk as soon as they are received.
 This is done to allow the transfer of large files even in very memory-constrained environments.\\
@@
 \subsubsection{Protocol}
-behem0th is independent from underg0und and defines its own network protocol.
+behem0th\cite{behem0th:Christoph Heiss} is independent from underg0und and defines its own network protocol.
 It is completely text-based, uses UTF-8\cite{UTF-8:F.
@@
 Bray Ed.} as format encoding.
-behem0th is designed around 'requests' $($see Figure ~\ref{fig:behem0th_request}$)$ and 'routes'.
+behem0th\cite{behem0th:Christoph Heiss} is designed around 'requests' $($see Figure ~\ref{fig:behem0th_request}$)$ and 'routes'.
 Each request is a JSON-formatted string and separated by a newline.
@@
 Josefsson} encoding is used.
-After the payload, there is again a newline to delimit payload and the next request.
+After each payload, there is a newline to delimit the payload and the next request.
 \\
@@
 \subsubsection{Security}
-Although MD5 is deprecated and known to suffers from extensive vulnerabilities, behem0th is designed to only run in a local network, which is controlled by the users of fl0w.
-This assumption also simplifies the implementation greatly.\\
+Although MD5 is deprecated and known to suffers from extensive vulnerabilities, behem0th\cite{behem0th:Christoph Heiss} is designed to only run in a local network, which is controlled by the users of fl0w\cite{fl0w:Philip Trauner}.
+This assumption also simplifies the implementation greatly.
 
 \subsection{dashb0ard}
-dashb0ard is a single-page web front-end designed to manage the fl0w fleet.
+dashb0ard\cite{dashb0ard:Sebastian Schaffler} is a single-page web front-end designed to manage the fl0w\cite{fl0w:Philip Trauner} fleet.
 It can be used to configure connected controllers and obtain sensor readouts as well as debug logs.
-It utilities the JavaScript version of undergr0und to retrieve data from fl0w, Vue.js\cite{Vue:Evan You} for its user interface, Bootstrap 3\cite{Bootstrap 3:Twitter Inc.} as a design baseline, Flot\cite{Flot:David Schnur} to display graphs and jQuery\cite{jQuery:jQuery Foundation} for additional DOM manipulation.
+It utilities the JavaScript version of undergr0und to retrieve data from fl0w\cite{fl0w:Philip Trauner}, Vue.js\cite{Vue:Evan You} for its user interface, Bootstrap 3\cite{Bootstrap 3:Twitter Inc.} as a design baseline, Flot\cite{Flot:David Schnur} to display graphs and jQuery\cite{jQuery:jQuery Foundation} for additional DOM manipulation.
 
+\begin{figure}[H]
+\centering
+\includegraphics[scale=0.3]{dashb0ard}
+\caption{The control and configuration page of dashb0ard\cite{Sublime Text 3:Sublime HQ}}
+\label{fig:dashb0ard_config}
+\end{figure}
+
+\begin{figure}[H]
+\centering
+\includegraphics[scale=0.25]{dashb0ard-sensor}
+\caption{The sensor readout page of dashb0ard\cite{Sublime Text 3:Sublime HQ}}
+\label{fig:dashb0ard_sensor}
+\end{figure}
 \subsection{edit0r}
-edit0r is the Sublime Text 3 plugin.
-It is modeled as a fl0w client and allows for remote robot management, source code synchronization as well as in-line sensor readouts.
-\\It also provides quick access to dashb0ard, which is required because the IP addresses of controllers are not always static.
-behem0th\cite{behem0th:Christoph Heiss} is embedded into edit0r and enables the source code synchronization.
+edit0r\cite{edit0r:Philip Trauner} is the Sublime Text 3\cite{Sublime Text 3:Sublime HQ} plugin.
+It is modeled as a fl0w\cite{fl0w:Philip Trauner} client and allows for remote robot management, source code synchronization as well as in-line sensor readouts.
+\\It also provides quick access to dashb0ard\cite{dashb0ard:Sebastian Schaffler}, which is required because the IP addresses of controllers are not always static.
+behem0th\cite{behem0th:Christoph Heiss} is embedded into edit0r\cite{edit0r:Philip Trauner} and enables the source code synchronization.
 In its current form only C programs are supported.\\
@@
 \subsubsection{Robot selection}
-fl0ws networking model allows for the management of multiple controllers without a direct connection to them.
+fl0ws\cite{fl0w:Philip Trauner} networking model allows for the management of multiple controllers without a direct connection to them.
 The controller hostname is utilised to identify the robots in the user-interface.
@@
 
+\begin{figure}[H]
+\centering
+\includegraphics[scale=0.6]{edit0r}
+\caption{Robot management interface in Sublime Text 3\cite{Sublime Text 3:Sublime HQ}}
+\label{fig:robot_management}
+\end{figure}
+
 \subsubsection{Robot management}
 Botball programs can be started (keyboard shortcut: F8) and/or stopped (keyboard shortcut: F9).
-Additionally, edit0r allows for modification of the controller hostname, playback of a sound for identification purposes, listing of running processes, power management functionality (reboot, shutdown) and running programs.\\
+Additionally, edit0r\cite{edit0r:Philip Trauner} allows for modification of the controller hostname, playback of a sound for identification purposes, listing of running processes, power management functionality (reboot, shutdown) and running programs.\\
 
@@
 Invocations of the functions "analog" and "digital" are located every time the content of a view changes and the parameters of the calls are grouped across views.
-edit0r subscribes to all required sensor ports by requesting them from the currently selected controller.
-The controller keeps track of all subscriptions to sensors and continuously transmits the appropriate values to the Sublime Text\cite{Sublime Text 3:Sublime HQ} plugin.
-\\Sublime Text \cite{Sublime Text 3:Sublime HQ} phantoms are created as soon as new sensor values are available.
-This approach has the disadvantage of higher than usual processor utilization by edit0r, because phantoms were primarily designed to display infrequently updated content.
+edit0r\cite{edit0r:Philip Trauner} subscribes to all required sensor ports by requesting them from the currently selected controller.
+The controller keeps track of all subscriptions to sensors and continuously transmits the appropriate values to the Sublime Text 3\cite{Sublime Text 3:Sublime HQ} plugin.
+\\Sublime Text 3 \cite{Sublime Text 3:Sublime HQ} phantoms are created as soon as new sensor values are available.
+This approach has the disadvantage of higher than usual processor utilization by edit0r\cite{edit0r:Philip Trauner}, because phantoms were primarily designed to display infrequently updated content.
 To partially circumvent this, sensor readouts can be disabled and are not enabled by default.\\
@@
 
+\begin{figure}[H]
+\centering
+\includegraphics[scale=0.7]{sensor-readouts}
+\caption{Inline sensor-readouts in Sublime Text 3\cite{Sublime Text 3:Sublime HQ}}
+\label{fig:inline_sensor_readouts}
+\end{figure}
+
 \subsection{r0adrunner}
-r0adrunner is the installer of fl0w.
-It is built to mimic a Wallaby controller software update to remain compatible with the preexisting update functionality found in Harrogate.
-It is implemented in Python 2.7, which is already installed on all Wallaby controllers but because fl0w utilizes features of Python 3.3 it installs a full-fledged precompiled version of Python 3.6.0.
-It also changes the Wallaby hostname to their unique manufacturing ID because fl0w utilizes hostnames to represent controllers in its user facing components.
+r0adrunner is the installer of fl0w\cite{fl0w:Philip Trauner}.
+It is built to mimic a Wallaby\cite{Wallaby Controller:KIPR} controller software update to remain compatible with the preexisting update functionality found in Harrogate\cite{Harrogate:KIPR}.
+It is implemented in Python\cite{Python:Python Foundation} 2.7, which is already installed on all Wallaby\cite{Wallaby Controller:KIPR} controllers but because fl0w\cite{fl0w:Philip Trauner} utilizes features of Python\cite{Python:Python Foundation} 3.3 it installs a full-fledged precompiled version of Python\cite{Python:Python Foundation} 3.6.0.
+It also changes the Wallaby\cite{Wallaby Controller:KIPR} hostname to their unique manufacturing ID because fl0w\cite{fl0w:Philip Trauner} utilizes hostnames to represent controllers in its user facing components.
 r0adrunner is distributed as an archive that has to be copied to an USB storage medium.
@@
 \subsection{fl0w}
-fl0w itself is the combination of all other components split into Wallaby client and server.\\
+fl0w\cite{fl0w:Philip Trauner} itself is the combination of all other components split into Wallaby\cite{Wallaby Controller:KIPR} client and server.\\
 
 \subsubsection{Wallaby client}
-The Wallaby client serves as an information source for sensor values, program output, as well as currently running processes. Additionally it exposes its own standard output for monitoring purposes.\\
+The Wallaby\cite{Wallaby Controller:KIPR} client serves as an information source for sensor values, program output, as well as currently running processes.
+Additionally it exposes its own standard output for monitoring purposes.\\
 
@@
 The server keeps track of all clients and provides means to acquire their peer IDs, which are used by undergr0und to target specific clients.
-Additionally it serves dashb0ard and handles program compilation.
+Additionally it serves dashb0ard\cite{dashb0ard:Sebastian Schaffler} and handles program compilation.
 It utilizes undergr0und for networking, behem0th for file-synchronization, and disc0very to determine if another server is already running in the network.
-In that situation the start is interrupted, the Wallaby client is started and it connects to the available server instance, otherwise server and client are started.
 \\
+In that situation the start is interrupted, the Wallaby\cite{Wallaby Controller:KIPR} client is started and it connects to the available server instance, otherwise server and client are started. \\
 
@@
 
-After prolonged testing it was deemed reasonable to claim that fl0w can improve the robotics development work-flow on Wallaby controllers.
+After prolonged testing it was deemed reasonable to claim that fl0w\cite{fl0w:Philip Trauner} can improve the robotics development work-flow on Wallaby\cite{Wallaby Controller:KIPR} controllers.
 
@@
 
-Support for Python as a robot programming language as well as basic remote procedure call functionality is the next development goal.
+Support for Python\cite{Python:Python Foundation} as a robot programming language as well as basic remote procedure call functionality is the next development goal.
 
@@
 \section*{Acknowledgment}
-The authors would like to thank the robotics team robot0nfire: Nico Kratky, Nico Leidenfrost,\\ Sebastian Schaffler, Christine Zeh, Sascha Zemann;\\ Dr.
-Michael Stifter for making the existence of our team possible; Daniel Maximilian Swoboda for answering all paper related questions; the KIPR development team without whom the Wallaby Controller would not exist.
+The authors would like to thank the robotics team robot0nfire: Nico Kratky, Nico Leidenfrost, Sebastian Schaffler, Christine Zeh, Sascha Zemann;\\ Dr.
+Michael Stifter for making the existence of our team possible; Daniel Maximilian Swoboda for answering all paper related questions; the KIPR development team without whom the Wallaby\cite{Wallaby Controller:KIPR} Controller would not exist.
 
 \begin{thebibliography}{1}
+
+\bibitem{fl0w:Philip Trauner}
+Philip Trauner, Christoph Heiss, Sebastian Schaffler, \emph{fl0w}, \url{https://github.com/robot0nfire/fl0w},\\ source code,
+accessed February 9th 2017
+
+\bibitem{Wallaby Controller:KIPR}
+KIPR, \emph{Wallaby Controller},  \url{http://botballstore.org/product/wallaby-controller}, \\ store page, accessed February 9th 2017
 
@@
 
-\bibitem{Python 3.3.6:Python Foundation}
-Python Foundation, \emph{Python 3.3.6}, \url{https://www.python.org/downloads/release/python-336/},\\ source code,
-accessed February 9th 2017
-
-\bibitem{behem0th:Christoph Heiss}
-Christoph Heiss, \emph{behem0th}, \url{https://github.com/robot0nfire/behem0th},\\ source code,
+\bibitem{Python:Python Foundation}
+Python Foundation, \emph{Python}, \url{https://www.python.org},\\ project page,
 accessed February 9th 2017
@@
 \bibitem{undergr0und:Philip Trauner}
-Philip Trauner, \emph{undergr0und}, \url{https://github.com/robot0nfire/fl0w/wiki/undergr0und},\\ implementation notes,
+Philip Trauner, \emph{undergr0und}, \url{https://github.com/robot0nfire/fl0w/wiki/undergr0und}, implementation notes,
 accessed February 9th 2017
@@
 
+\bibitem{undergr0und.js:Philip Trauner}
+Philip Trauner, \emph{undergr0und},\\ \url{https://github.com/robot0nfire/undergr0und.js}, source code, \\accessed February 9th 2017
+
+\bibitem{node-jspack:Peter Griess}
+Peter Griess, \emph{node-jspack}, \url{https://github.com/pgriess/node-jspack},\\ source code,
+accessed February 9th 2017
+
+\bibitem{Node.js:Node.js Foundation}
+Node.js Foundation, \emph{Node.js}, \url{https://nodejs.org},\\ product page,
+accessed February 9th 2017
+
+\bibitem{browserify:James Halliday}
+James Halliday, \emph{browserify}, \url{http://browserify.org/},\\ product page,
+accessed February 9th 2017
+
+\bibitem{JSON:T. Bray Ed.}
+T. Bray, Ed., \emph{JSON}, \url{https://tools.ietf.org/html/rfc7159},\\ request for comment,
+accessed February 9th 2017
+
 \bibitem{watchdog:Yesudeep Mangalapilly}
-Yesudeep Mangalapilly, \emph{watchdog}, \url{https://github.com/gorakhargosh/watchdog},\\ source code,
+Yesudeep Mangalapilly, \emph{watchdog}, \url{https://github.com/gorakhargosh/watchdog}, source code,
 accessed February 9th 2017
@@
 
-\bibitem{JSON:T. Bray Ed.}
-T. Bray, Ed., \emph{JSON}, \url{https://tools.ietf.org/html/rfc7159},\\ request for comment,
-accessed February 9th 2017
-
 \bibitem{Base64:S. Josefsson}
@@
 
-\bibitem{bottle.py:Marcel Hellkamp}
-Marcel Hellkamp, \emph{bottle.py}, \url{https://github.com/bottlepy/bottle},\\ source code,
-accessed February 9th 2017
+\bibitem{dashb0ard:Sebastian Schaffler}
+Sebastian Schaffler, Philip Trauner, \emph{dashb0ard}, \url{https://github.com/robot0nfire/dashb0ard},\\ source code,
+accessed March 16th 2017
+
+\bibitem{Vue:Evan You}
+Evan You, \emph{Vue.js}, \url{https://vuejs.org/},\\ product page,
+accessed March 16th 2017
+
+\bibitem{Bootstrap 3:Twitter Inc.}
+Twitter, Inc., \emph{Bootstrap 3}, \url{http://getbootstrap.com},\\ product page,
+accessed March 16th 2017
 
@@
 
-\bibitem{browserify:James Halliday}
-James Halliday, \emph{browserify}, \url{http://browserify.org/},\\ product page,
+\bibitem{edit0r:Philip Trauner}
+Philip Trauner, \emph{edit0r}, \url{https://github.com/robot0nfire/fl0w/tree/master/Sublime/fl0w},\\ source code,
 accessed February 9th 2017
 
-\bibitem{Node.js:Node.js Foundation}
-Node.js Foundation, \emph{Node.js}, \url{https://nodejs.org},\\ product page,
+\bibitem{behem0th:Christoph Heiss}
+Christoph Heiss, \emph{behem0th}, \url{https://github.com/robot0nfire/behem0th},\\ source code,
 accessed February 9th 2017
-
-\bibitem{Bootstrap 3:Twitter Inc.}
-Twitter, Inc., \emph{Bootstrap 3}, \url{http://getbootstrap.com},\\ product page,
-accessed March 16th 2017
-
-\bibitem{Vue:Evan You}
-Evan You, \emph{Vue.js}, \url{https://vuejs.org/},\\ product page,
-accessed March 16th 2017
 

### 2017-03-30 paper.tex
Streched out Introduction, readded section for disc0very

@@
 \begin{abstract}
-This publication introduces fl0w\cite{fl0w:Philip Trauner}, an alternative\\ development environment for the KIPR Wallaby\cite{Wallaby Controller:KIPR}.\\ The aim of fl0w\cite{fl0w:Philip Trauner} is to improve the robotics program development experience.
+This publication introduces fl0w\cite{fl0w:Philip Trauner}, an alternative\\ development environment for the KIPR Wallaby\cite{Wallaby Controller:KIPR}.\\ The aim of fl0w\cite{fl0w:Philip Trauner} is to improve the Botball program development experience.
 It focuses on the components that make up fl0w\cite{fl0w:Philip Trauner}, namely a file synchronization protocol that maintains a consistent state across all connected controllers, a route based and data type preserving network protocol with peer-to-peer piping capabilities, a discovery protocol that connects all controllers together automatically, a Sublime Text 3\cite{Sublime Text 3:Sublime HQ} plugin which enables in-line sensor readouts, program execution, program editing, and keyboard shortcuts, and a browser-based management front-end to manage the controller fleet.\\
@@
 All fl0w\cite{fl0w:Philip Trauner} components emphasize shared code and are therefor written in Python\cite{Python:Python Foundation} 3.3.6 to remain compatible with the Sublime Text 3\cite{Sublime Text 3:Sublime HQ} plugin environment.
-Python\cite{Python:Python Foundation} was chosen as the implementation language for fl0w\cite{fl0w:Philip Trauner} because of its rich standard library and its lightweight virtual machine that can run on a Wallaby\cite{Wallaby Controller:KIPR} controller with acceptable speed.
+\\Python\cite{Python:Python Foundation} was chosen as the implementation language for fl0w\cite{fl0w:Philip Trauner} because of its rich standard library and its lightweight virtual machine that can run on a Wallaby\cite{Wallaby Controller:KIPR} controller with acceptable speed.
 A pre-compiled version of Python\cite{Python:Python Foundation} is bundled with the fl0w\cite{fl0w:Philip Trauner} installer, r0adrunner, because it is not present on the Wallaby\cite{Wallaby Controller:KIPR} by default.
-All fl0w\cite{fl0w:Philip Trauner} components are designed as libraries to allow for integration into other projects.
+\\All fl0w\cite{fl0w:Philip Trauner} components are designed as libraries to allow for integration into other projects.
 fl0w\cite{fl0w:Philip Trauner} utilities a client-server networking model with random server assignment.
+Client-server was chosen because the server can act as a data source for all clients.
 
@@
 \subsection{undergr0und}
-undergr0und\cite{undergr0und:Philip Trauner} is an asynchronous, route based, largely programming language agnostic, and data type preserving network protocol with peer-to-peer piping capabilities.
+undergr0und\cite{undergr0und:Philip Trauner} is an asynchronous, route based, and data type preserving network protocol with peer-to-peer piping capabilities.
 It automatically converts data into a transferable format and prepends binary headers to allow for reconstruction on the other end.
@@
 undergr0und.js\cite{undergr0und.js:Philip Trauner} is the feature complete client-side JavaScript port of undergr0und\cite{undergr0und:Philip Trauner} that was required for dashb0ard\cite{dashb0ard:Sebastian Schaffler}, the browser-based front-end for fl0w\cite{fl0w:Philip Trauner}.
-It utilizes node-jspack\cite{node-jspack:Peter Griess} to unpack the binary messages it receives from the undergr0und\cite{undergr0und:Philip Trauner} server.
+\\It utilizes node-jspack\cite{node-jspack:Peter Griess} to unpack the binary messages it receives from the undergr0und\cite{undergr0und:Philip Trauner} server.
 It is based on the Python\cite{Python:Python Foundation} version but does not implement the server because there is currently no need for that functionality.
-undergr0und.js can run be used in Node.js\cite{Node.js:Node.js Foundation} as well as browsers that support WebSockets\cite{The WebSocket Protocol:A.
+\\undergr0und.js can run be used in Node.js\cite{Node.js:Node.js Foundation} as well as browsers that support WebSockets\cite{The WebSocket Protocol:A.
 Melnikov}.
@@
 Invoked with the {\color{deepgreen}"pipe"} call.
-Clients can be targeted with unique IDs that are generated randomly for all connected peers by the server.
+\\Clients can be targeted with unique IDs that are generated randomly for all connected peers by the server.
 There is no predefined mechanism in the network protocol that exposed these peer IDs, the application using undergr0und\cite{undergr0und:Philip Trauner} has to provide a way of making them available.
 This approach allows for more flexibility if additional peer-metadata has to be provided.
-Pipe messages are packaged inside regular route messages with additional headers in the data segment.
+\\Pipe messages are packaged inside regular route messages with additional headers in the data segment.
 A server route called {\color{deepgreen}"pipe"} unpacks the regular and the extended headers and forwards the message to the targeted peer.
@@
 behem0th\cite{behem0th:Christoph Heiss} is a continuous network file synchronization protocol developed out of the need for an embeddable solution that would not require an additional background program to be present on the system running Sublime Text 3\cite{Sublime Text 3:Sublime HQ}, instead utilizing its plugin environment.
-It uses a client-server networking model without peer-to-peer capabilities to stay in line with undergr0und.
+\\It uses a client-server networking model without peer-to-peer capabilities to stay in line with undergr0und.
 It uses regular sockets instead of WebSockets\cite{The WebSocket Protocol:A.
@@
 \subsection{dashb0ard}
-dashb0ard\cite{dashb0ard:Sebastian Schaffler} is a single-page web front-end designed to manage the fl0w\cite{fl0w:Philip Trauner} fleet.
-It can be used to configure connected controllers and obtain sensor readouts as well as debug logs.
-It utilities the JavaScript version of undergr0und to retrieve data from fl0w\cite{fl0w:Philip Trauner}, Vue.js\cite{Vue:Evan You} for its user interface, Bootstrap 3\cite{Bootstrap 3:Twitter Inc.} as a design baseline, Flot\cite{Flot:David Schnur} to display graphs and jQuery\cite{jQuery:jQuery Foundation} for additional DOM manipulation.
+dashb0ard\cite{dashb0ard:Sebastian Schaffler} is a single-page web front-end designed to manage the fl0w\cite{fl0w:Philip Trauner} fleet.\\ It can be used to configure connected controllers and obtain sensor readouts as well as debug logs.
+\\It utilities the JavaScript version of undergr0und to retrieve data from fl0w\cite{fl0w:Philip Trauner}, Vue.js\cite{Vue:Evan You} for its user interface, Bootstrap 3\cite{Bootstrap 3:Twitter Inc.} as a design baseline, Flot\cite{Flot:David Schnur} to display graphs and jQuery\cite{jQuery:jQuery Foundation} for additional DOM manipulation.
 
@@
 \includegraphics[scale=0.6]{edit0r}
-\caption{Robot management interface in Sublime Text 3\cite{Sublime Text 3:Sublime HQ}}
+\caption{edit0rs\cite{edit0r:Philip Trauner} robot management interface in Sublime Text 3\cite{Sublime Text 3:Sublime HQ}}
 \label{fig:robot_management}
@@
 \includegraphics[scale=0.7]{sensor-readouts}
-\caption{Inline sensor-readouts in Sublime Text 3\cite{Sublime Text 3:Sublime HQ}}
+\caption{edit0rs\cite{edit0r:Philip Trauner} inline sensor-readouts in Sublime Text 3\cite{Sublime Text 3:Sublime HQ}}
 \label{fig:inline_sensor_readouts}
@@
 r0adrunner is the installer of fl0w\cite{fl0w:Philip Trauner}.
-It is built to mimic a Wallaby\cite{Wallaby Controller:KIPR} controller software update to remain compatible with the preexisting update functionality found in Harrogate\cite{Harrogate:KIPR}.
+\\It is built to mimic a Wallaby\cite{Wallaby Controller:KIPR} controller software update to remain compatible with the preexisting update functionality found in Harrogate\cite{Harrogate:KIPR}.
 It is implemented in Python\cite{Python:Python Foundation} 2.7, which is already installed on all Wallaby\cite{Wallaby Controller:KIPR} controllers but because fl0w\cite{fl0w:Philip Trauner} utilizes features of Python\cite{Python:Python Foundation} 3.3 it installs a full-fledged precompiled version of Python\cite{Python:Python Foundation} 3.6.0.
-It also changes the Wallaby\cite{Wallaby Controller:KIPR} hostname to their unique manufacturing ID because fl0w\cite{fl0w:Philip Trauner} utilizes hostnames to represent controllers in its user facing components.
+\\It also changes the Wallaby\cite{Wallaby Controller:KIPR} hostname to their unique manufacturing ID because fl0w\cite{fl0w:Philip Trauner} utilizes hostnames to represent controllers in its user facing components.
 r0adrunner is distributed as an archive that has to be copied to an USB storage medium.
+
+\subsection{disc0very}
 
@@
 
-After prolonged testing it was deemed reasonable to claim that fl0w\cite{fl0w:Philip Trauner} can improve the robotics development work-flow on Wallaby\cite{Wallaby Controller:KIPR} controllers.
+After prolonged testing it was deemed reasonable to claim that fl0w\cite{fl0w:Philip Trauner} can improve the Botball development work-flow on Wallaby\cite{Wallaby Controller:KIPR} controllers.
 

### 2017-03-30 paper.tex
Corrected email, split up sections, more label text for figures, reintroduced disc0very

@@
 
-\title{fl0w 2.0 - a development environment for the\\ KIPR Wallaby}
+\title{fl0w - a development environment for the\\ KIPR Wallaby}
 \author{\IEEEauthorblockN{Philip Trauner, Christoph Heiss, Sebastian Schaffler, Nico Kratky, Nico Leidenfrost, Christine Zeh, Sascha Zemann}
@@
 Wiener Neustadt, Austria\\
-Email: philip.trauner@arztpraxis.io, me@christoph-heiss.me, se.schaffler@gmail.com, \\nico@nicokratky.me, leidenfrost.nico@gmail.com, krixizeh@gmail.com, sascha.zemann@gmail.com}
+Email: philip.trauner@arztpraxis.io, me@christoph-heiss.me, se.schaffler@gmail.com, \\nico@nicokratky.me, leidenfrost.nico@gmail.com, zeh.chrisi@gmail.com, sascha.zemann@gmail.com}
 }
@@
 fl0w\cite{fl0w:Philip Trauner} was developed out of a need for a fast, reliable and wireless workflow solution that can compete with the currently available offerings like Harrogate\cite{Harrogate:KIPR}.
-Its goals are to transform the connected controllers into a redundant fleet of logical units that share the same binaries and source code, real-time in-line sensor readouts, programming as well as robot management inside Sublime Text 3\cite{Sublime Text 3:Sublime HQ}, a browser-based front-end and the ability to connect to a wireless access point.
+Its goals are to transform the connected controllers into a redundant fleet of logical units that share the same binaries and source code, real-time in-line sensor readouts, programming as well as robot management inside Sublime Text 3\cite{Sublime Text 3:Sublime HQ}, and a browser-based front-end.
 
@@
 \begin{table}[H]
-\caption{The binary encoding of undergr0und (in bytes)}
+\caption{The binary encoding of messages in undergr0und (in bytes)}
 \centering
@@
 \end{python}
-\caption{Creation of exchange maps}
+\caption{Creation of exchange maps used to lower bandwidth requirements}
 \end{figure}
@@
 \end{json}
-\caption{behem0th request}
+\caption{behem0th request encoding in JSON\cite{JSON:T. Bray Ed.}}
 \label{fig:behem0th_request}
@@
 \subsection{disc0very}
+disc0very is the networked controller discovery protocol of fl0w\cite{fl0w:Philip Trauner}. It utilizes UDP broadcasts to find and advertise controllers.
 
@@
 Security was never a design goal, instead relying on network interface level security was chosen to save time. This assumption will cause problems in densely populated wireless networks.
+
+Many edge cases can and will occur while performing continuous file-synchronization with an undetermined amount of clients across multiple operating-systems and file-systems.
 

### 2017-03-30 paper.tex
Write something about disc0very

@@
 \subsection{disc0very}
-disc0very is the networked controller discovery protocol of fl0w\cite{fl0w:Philip Trauner}. It utilizes UDP broadcasts to find and advertise controllers.
+disc0very is the controller discovery protocol of fl0w\cite{fl0w:Philip Trauner}.
+It utilizes UDP broadcasts to find and advertise controllers.
+It enables all fl0w\cite{fl0w:Philip Trauner} clients to connect together all the different Wallaby\cite{Wallaby Controller:KIPR} controllers and Sublime Text 3\cite{Sublime Text 3:Sublime HQ} clients automatically without any user interaction.\\
+
+\subsubsection{discovery process}
+When fl0w starts up, discovery will at first listen for a certain timeout period for other controllers on the broadcast.
+If it detects a already running fl0w\cite{fl0w:Philip Trauner} server in the local network, it will simply connect to that server and become a regular client.
+If not, the controller itself will become the server and advertise it on the broadcast.
 

### 2017-03-30 paper.tex
Improved disc0very section, added figure and error recovery

--- 2017-03-30 paper.tex
@@
 \subsection{disc0very}
-disc0very is the networked controller discovery protocol of fl0w\cite{fl0w:Philip Trauner}. It utilizes UDP broadcasts to find and advertise controllers.
+disc0very\cite{disc0very:Christoph Heiss} is the LAN discovery protocol of fl0w\cite{fl0w:Philip Trauner}.
+It relies on UDP\cite{UDP:J.
+Postel} broadcasts to coordinate server and client assignment.
+Wallaby controller instances as well as the Sublime Text 3\cite{Sublime Text 3:Sublime HQ} plugin edit0r\cite{edit0r:Philip Trauner} utilize it to determine if there is already an active fl0w server on the network upon startup without user interaction.
+
+\subsubsection{Discovery process}
+Upon launch disc0very\cite{disc0very:Christoph Heiss} listens for advertisements from an already running fl0w\cite{fl0w:Philip Trauner} server.
+If an advertisement is received the client-mode is engaged and a connection to the server is established.
+If no advertisement has been received after 2000ms server-mode is engaged.
+Server-mode can be disabled for clients that do not have the capability to become a server (for example edit0r\cite{edit0r:Philip Trauner}).
+
+\begin{figure}[H]
+\centering
+\begin{json}
+{
+    "address": "<address>",
+    "port": "<port>"
+}
+\end{json}
+\caption{disc0very advertisement encoding in JSON\cite{JSON:T. Bray Ed.}}
+\label{fig:discovery_advertisement}
+\end{figure}
+
+\subsubsection{Error recovery}
+disc0very\cite{disc0very:Christoph Heiss} actively listens for advertisements in server-mode to prevent more than one running server on the network.
+If a server receives an advertisement from another server both shutdown and return to discovery mode.
 
@@
 \bibitem{dashb0ard:Sebastian Schaffler}
-Sebastian Schaffler, Philip Trauner, \emph{dashb0ard}, \url{https://github.com/robot0nfire/dashb0ard},\\ source code,
+Sebastian Schaffler, Philip Trauner, \emph{dashb0ard}, \url{https://github.com/robot0nfire/dashb0ard}, source code,
 accessed March 16th 2017
@@
 \bibitem{edit0r:Philip Trauner}
-Philip Trauner, \emph{edit0r}, \url{https://github.com/robot0nfire/fl0w/tree/master/Sublime/fl0w},\\ source code,
-accessed February 9th 2017
+Philip Trauner, \emph{edit0r}, \url{https://github.com/robot0nfire/fl0w/tree/master/Sublime/fl0w},\\ source code, accessed February 9th 2017
+
+\bibitem{disc0very:Christoph Heiss}
+Christoph Heiss, \emph{disc0very}, \url{https://github.com/robot0nfire/fl0w/blob/master/Shared/Disc0very.py},\\ source code, accessed March 30th 2017
+
+\bibitem{UDP:J. Postel}
+J. Postel, \emph{UDP}, \url{https://www.ietf.org/rfc/rfc768.txt},\\ request for comment, accessed March 30th 2017
 

### 2017-04-01 paper.tex
Added citation to disc0very figure
(Hopefully) final changes

@@
-\documentclass[conference]{IEEEtran}
+\documentclass[conference,a4paper]{IEEEtran}
 
@@
 \begin{abstract}
-This publication introduces fl0w\cite{fl0w:Philip Trauner}, an alternative\\ development environment for the KIPR Wallaby\cite{Wallaby Controller:KIPR}.\\ The aim of fl0w\cite{fl0w:Philip Trauner} is to improve the Botball program development experience.
-It focuses on the components that make up fl0w\cite{fl0w:Philip Trauner}, namely a file synchronization protocol that maintains a consistent state across all connected controllers, a route based and data type preserving network protocol with peer-to-peer piping capabilities, a discovery protocol that connects all controllers together automatically, a Sublime Text 3\cite{Sublime Text 3:Sublime HQ} plugin which enables in-line sensor readouts, program execution, program editing, and keyboard shortcuts, and a browser-based management front-end to manage the controller fleet.\\
+This publication introduces fl0w, an alternative development environment and monitoring solution for the KIPR Wallaby.
+The aim of fl0w is to improve the Botball program development experience.
+It focuses on the components that make up fl0w, namely a file synchronization protocol that maintains a consistent state across all connected controllers, a route based and data type preserving network protocol with peer-to-peer piping capabilities, a discovery protocol that connects all controllers together automatically, a Sublime Text 3 plugin which enables in-line sensor readouts, program execution, program editing, and keyboard shortcuts, and a browser-based management front-end to manage the controller fleet.\\
 \end{abstract}
@@
 \begin{IEEEkeywords}
-file synchronization, networking, LAN discovery, development environment
+file synchronization, networking, LAN discovery, development environment, monitoring
 \end{IEEEkeywords}
@@
 All fl0w\cite{fl0w:Philip Trauner} components emphasize shared code and are therefor written in Python\cite{Python:Python Foundation} 3.3.6 to remain compatible with the Sublime Text 3\cite{Sublime Text 3:Sublime HQ} plugin environment.
-\\Python\cite{Python:Python Foundation} was chosen as the implementation language for fl0w\cite{fl0w:Philip Trauner} because of its rich standard library and its lightweight virtual machine that can run on a Wallaby\cite{Wallaby Controller:KIPR} controller with acceptable speed.
-A pre-compiled version of Python\cite{Python:Python Foundation} is bundled with the fl0w\cite{fl0w:Philip Trauner} installer, r0adrunner, because it is not present on the Wallaby\cite{Wallaby Controller:KIPR} by default.
-\\All fl0w\cite{fl0w:Philip Trauner} components are designed as libraries to allow for integration into other projects.
-fl0w\cite{fl0w:Philip Trauner} utilities a client-server networking model with random server assignment.
+\\Python was chosen as the implementation language for fl0w because of its rich standard library and its lightweight virtual machine that can run on a Wallaby\cite{Wallaby Controller:KIPR} controller with acceptable speed.
+A pre-compiled version of Python is bundled with the fl0w installer, r0adrunner, because it is not present on the Wallaby by default.
+\\All fl0w components are designed as libraries to allow for integration into other projects.
+fl0w utilities a client-server networking model with random server assignment.
 Client-server was chosen because the server can act as a data source for all clients.
@@
 
-The Python\cite{Python:Python Foundation} version is built on top of a fork of ws4py\cite{ws4py:Philip Trauner} and the JavaScript version utilizes regular WebSockets\cite{The WebSocket Protocol:A.
+The Python\cite{Python:Python Foundation} version is built on top of a fork of ws4py\cite{ws4py:Philip Trauner} and the JavaScript\cite{ECMAScript:Ecma} version utilizes regular WebSockets\cite{The WebSocket Protocol:A.
 Melnikov} in arraybuffer mode.
-It was created to mitigate the problems fl0ws\cite{fl0w:Philip Trauner}explorative development style created.
+It was created because the requirements for fl0ws\cite{fl0w:Philip Trauner} network protocol specification changed constantly and a dynamic approach to networking was required.
 Instead of one monolithic network protocol, undergr0und emphasizes small sub protocols.
-This was done because all monolithic designs became too inconsistent over time.
-undergr0und\cite{undergr0und:Philip Trauner} manages itself through its own concepts.\\
+undergr0und manages itself through its own concepts.\\
 
 \subsubsection{undergr0und.js}
-undergr0und.js\cite{undergr0und.js:Philip Trauner} is the feature complete client-side JavaScript port of undergr0und\cite{undergr0und:Philip Trauner} that was required for dashb0ard\cite{dashb0ard:Sebastian Schaffler}, the browser-based front-end for fl0w\cite{fl0w:Philip Trauner}.
-\\It utilizes node-jspack\cite{node-jspack:Peter Griess} to unpack the binary messages it receives from the undergr0und\cite{undergr0und:Philip Trauner} server.
+undergr0und.js\cite{undergr0und.js:Philip Trauner} is the feature complete client-side JavaScript\cite{ECMAScript:Ecma} port of undergr0und\cite{undergr0und:Philip Trauner} that was required for dashb0ard\cite{dashb0ard:Sebastian Schaffler}, the browser-based front-end for fl0w\cite{fl0w:Philip Trauner}.
+\\It utilizes node-jspack\cite{node-jspack:Peter Griess} to unpack the binary messages it receives from the undergr0und server.
 It is based on the Python\cite{Python:Python Foundation} version but does not implement the server because there is currently no need for that functionality.
-\\undergr0und.js can run be used in Node.js\cite{Node.js:Node.js Foundation} as well as browsers that support WebSockets\cite{The WebSocket Protocol:A.
+\\undergr0und.js can be used in Node.js\cite{Node.js:Node.js Foundation} as well as browsers that support WebSockets\cite{The WebSocket Protocol:A.
 Melnikov}.
@@
 Bray Ed.} is used to transfer lists and dictionaries, and regular ASCII encoded strings are utilized to transfer integers, floats, null/none types and strings.
+JSON was chosen because it can be serialized and parsed by Python\cite{Python:Python Foundation} as well as JavaScript\cite{ECMAScript:Ecma}.
 
@@
 After that, files get synchronized to other clients as soon as a file-system event happens.
-Synchronization conflicts are resolved on the server and it is possible to use behem0th\cite{behem0th:Christoph Heiss} with a theoretically indefinite amount of clients.\\
+Synchronization conflicts are resolved on the server and it is possible to use behem0th with a theoretically indefinite amount of clients.\\
 
@@
 Bray Ed.} as format encoding.
-behem0th\cite{behem0th:Christoph Heiss} is designed around 'requests' $($see Figure ~\ref{fig:behem0th_request}$)$ and 'routes'.
+behem0th is designed around 'requests' $($see Figure ~\ref{fig:behem0th_request}$)$ and 'routes'.
 Each request is a JSON-formatted string and separated by a newline.
@@
 dashb0ard\cite{dashb0ard:Sebastian Schaffler} is a single-page web front-end designed to manage the fl0w\cite{fl0w:Philip Trauner} fleet.\\ It can be used to configure connected controllers and obtain sensor readouts as well as debug logs.
-\\It utilities the JavaScript version of undergr0und to retrieve data from fl0w\cite{fl0w:Philip Trauner}, Vue.js\cite{Vue:Evan You} for its user interface, Bootstrap 3\cite{Bootstrap 3:Twitter Inc.} as a design baseline, Flot\cite{Flot:David Schnur} to display graphs and jQuery\cite{jQuery:jQuery Foundation} for additional DOM manipulation.
+\\It utilities undergr0und.js\cite{undergr0und.js:Philip Trauner} to retrieve data from fl0w, Vue.js\cite{Vue:Evan You} for its user interface, Bootstrap 3\cite{Bootstrap 3:Twitter Inc.} as a design baseline, Flot\cite{Flot:David Schnur} to display graphs and jQuery\cite{jQuery:jQuery Foundation} for additional DOM manipulation.
 
@@
 \\It also provides quick access to dashb0ard\cite{dashb0ard:Sebastian Schaffler}, which is required because the IP addresses of controllers are not always static.
-behem0th\cite{behem0th:Christoph Heiss} is embedded into edit0r\cite{edit0r:Philip Trauner} and enables the source code synchronization.
+behem0th\cite{behem0th:Christoph Heiss} is embedded into edit0r and enables the source code synchronization.
 In its current form only C programs are supported.\\
@@
 The controller keeps track of all subscriptions to sensors and continuously transmits the appropriate values to the Sublime Text 3\cite{Sublime Text 3:Sublime HQ} plugin.
-\\Sublime Text 3 \cite{Sublime Text 3:Sublime HQ} phantoms are created as soon as new sensor values are available.
-This approach has the disadvantage of higher than usual processor utilization by edit0r\cite{edit0r:Philip Trauner}, because phantoms were primarily designed to display infrequently updated content.
+\\Sublime Text 3 phantoms are created as soon as new sensor values are available.
+This approach has the disadvantage of higher than usual processor utilization by edit0r, because phantoms were primarily designed to display infrequently updating content.
 To partially circumvent this, sensor readouts can be disabled and are not enabled by default.\\
@@
 \\It is built to mimic a Wallaby\cite{Wallaby Controller:KIPR} controller software update to remain compatible with the preexisting update functionality found in Harrogate\cite{Harrogate:KIPR}.
-It is implemented in Python\cite{Python:Python Foundation} 2.7, which is already installed on all Wallaby\cite{Wallaby Controller:KIPR} controllers but because fl0w\cite{fl0w:Philip Trauner} utilizes features of Python\cite{Python:Python Foundation} 3.3 it installs a full-fledged precompiled version of Python\cite{Python:Python Foundation} 3.6.0.
-\\It also changes the Wallaby\cite{Wallaby Controller:KIPR} hostname to their unique manufacturing ID because fl0w\cite{fl0w:Philip Trauner} utilizes hostnames to represent controllers in its user facing components.
+It is implemented in Python\cite{Python:Python Foundation} 2.7, which is already installed on all Wallaby controllers.
+A full-fledged precompiled version of Python 3.6.0 is installed by r0adrunner because fl0w utilizes features of Python 3.3.6.
+\\It also changes the Wallaby hostname to their unique manufacturing ID because fl0w uses hostnames to represent controllers in its user facing components.
 r0adrunner is distributed as an archive that has to be copied to an USB storage medium.
@@
 Postel} broadcasts to coordinate server and client assignment.
-Wallaby controller instances as well as the Sublime Text 3\cite{Sublime Text 3:Sublime HQ} plugin edit0r\cite{edit0r:Philip Trauner} utilize it to determine if there is already an active fl0w server on the network upon startup without user interaction.
+Wallaby controller instances as well as the Sublime Text 3\cite{Sublime Text 3:Sublime HQ} plugin edit0r\cite{edit0r:Philip Trauner} make use of it to determine if there is already an active fl0w server on the network upon startup without user interaction.
 
@@
 If an advertisement is received the client-mode is engaged and a connection to the server is established.
-If no advertisement has been received after 2000ms server-mode is engaged.
-Server-mode can be disabled for clients that do not have the capability to become a server (for example edit0r\cite{edit0r:Philip Trauner}).
+If no advertisement has been received after 2s server-mode is engaged.
+Server-mode can be disabled for clients that do not have the capability to become a server, for example edit0r\cite{edit0r:Philip Trauner}).
 
@@
 \end{json}
-\caption{disc0very advertisement encoding in JSON\cite{JSON:T. Bray Ed.}}
+\caption{disc0very\cite{disc0very:Christoph Heiss} advertisement encoding in JSON\cite{JSON:T. Bray Ed.}}
 \label{fig:discovery_advertisement}
@@
 Additionally it serves dashb0ard\cite{dashb0ard:Sebastian Schaffler} and handles program compilation.
-It utilizes undergr0und for networking, behem0th for file-synchronization, and disc0very to determine if another server is already running in the network.
+It utilizes undergr0und for networking, behem0th for file-synchronization, and disc0very\cite{disc0very:Christoph Heiss} to determine if another server is already running in the network.
 \\
@@
 \section{Conclusion}
-
 After prolonged testing it was deemed reasonable to claim that fl0w\cite{fl0w:Philip Trauner} can improve the Botball development work-flow on Wallaby\cite{Wallaby Controller:KIPR} controllers.
+Experienced Botball teams that would rather program in native tools than the browser-based Harrogate and want to observe their sensor-readouts in realtime can benefit from fl0w.
 
@@
 
-Many edge cases can and will occur while performing continuous file-synchronization with an undetermined amount of clients across multiple operating-systems and file-systems.
+There is a high amount of complexity involved when performing continuous file-synchronization with an undetermined amount of clients across multiple operating-systems and file-systems.
 
@@
 
-% section* for acknowledgment
 \section*{Acknowledgment}
@@
 
-\bibitem{Wallaby Controller:KIPR}
-KIPR, \emph{Wallaby Controller},  \url{http://botballstore.org/product/wallaby-controller}, \\ store page, accessed February 9th 2017
+\bibitem{Harrogate:KIPR}
+KIPR, \emph{Harrogate}, \url{https://github.com/kipr/harrogate},\\ source code,
+accessed February 9th 2017
 
@@
 
-\bibitem{Harrogate:KIPR}
-KIPR, \emph{Harrogate}, \url{https://github.com/kipr/harrogate},\\ source code,
-accessed February 9th 2017
-
 \bibitem{Python:Python Foundation}
@@
 accessed February 9th 2017
+
+\bibitem{Wallaby Controller:KIPR}
+KIPR, \emph{Wallaby Controller},  \url{http://botballstore.org/product/wallaby-controller}, \\ store page, accessed February 9th 2017
 
@@
 accessed February 9th 2017
+
+\bibitem{ECMAScript:Ecma}
+Ecma International, \emph{ECMAScript}, \url{https://www.ecma-international.org/ecma-262/7.0/index.html},\\ language specification,
+accessed February 12th 2017
 

### 2017-04-01 paper.tex
Fixed references leaking onto 5th page

@@
 behem0th\cite{behem0th:Christoph Heiss} is independent from underg0und and defines its own network protocol.
-It is completely text-based, uses UTF-8\cite{UTF-8:F.
-Yergeau} for character encoding and JSON\cite{JSON:T.
+It is completely text-based, uses UTF-8 for character encoding and JSON\cite{JSON:T.
 Bray Ed.} as format encoding.
@@
 If no advertisement has been received after 2s server-mode is engaged.
-Server-mode can be disabled for clients that do not have the capability to become a server, for example edit0r\cite{edit0r:Philip Trauner}).
 
@@
 \bibitem{fl0w:Philip Trauner}
-Philip Trauner, Christoph Heiss, Sebastian Schaffler, \emph{fl0w}, \url{https://github.com/robot0nfire/fl0w},\\ source code,
+Philip Trauner, Christoph Heiss, Sebastian Schaffler, \emph{fl0w}, \url{https://github.com/robot0nfire/fl0w}, source code,
 accessed February 9th 2017
@@
 \bibitem{Harrogate:KIPR}
-KIPR, \emph{Harrogate}, \url{https://github.com/kipr/harrogate},\\ source code,
+KIPR, \emph{Harrogate}, \url{https://github.com/kipr/harrogate}, \\ source code,
 accessed February 9th 2017
@@
 \bibitem{Wallaby Controller:KIPR}
-KIPR, \emph{Wallaby Controller},  \url{http://botballstore.org/product/wallaby-controller}, \\ store page, accessed February 9th 2017
+KIPR, \emph{Wallaby Controller},\\  \url{http://botballstore.org/product/wallaby-controller}, store page, accessed February 9th 2017
 
@@
 \bibitem{ECMAScript:Ecma}
-Ecma International, \emph{ECMAScript}, \url{https://www.ecma-international.org/ecma-262/7.0/index.html},\\ language specification,
-accessed February 12th 2017
+Ecma International, \emph{ECMAScript}, \\\url{https://www.ecma-international.org/ecma-262/7.0/index.html}, language specification, accessed February 12th 2017
 
@@
 
-\bibitem{UTF-8:F. Yergeau}
-F. Yergeau, \emph{UTF-8}, \url{https://tools.ietf.org/html/rfc3629},\\ request for comment,
-accessed March 22nd 2017
-
 \bibitem{Base64:S. Josefsson}
@@
 \bibitem{edit0r:Philip Trauner}
-Philip Trauner, \emph{edit0r}, \url{https://github.com/robot0nfire/fl0w/tree/master/Sublime/fl0w},\\ source code, accessed February 9th 2017
+Philip Trauner, \emph{edit0r}, \url{https://github.com/robot0nfire/fl0w/tree/master/Sublime/fl0w}, source code, accessed February 9th 2017
 
 \bibitem{disc0very:Christoph Heiss}
-Christoph Heiss, \emph{disc0very}, \url{https://github.com/robot0nfire/fl0w/blob/master/Shared/Disc0very.py},\\ source code, accessed March 30th 2017
+Christoph Heiss, \emph{disc0very}, \url{https://github.com/robot0nfire/fl0w/blob/master/Shared/Disc0very.py}, source code, accessed March 30th 2017
 

### 2017-04-01 paper.tex
Final touches

@@
 \title{fl0w - a development environment for the\\ KIPR Wallaby}
-\author{\IEEEauthorblockN{Philip Trauner, Christoph Heiss, Sebastian Schaffler, Nico Kratky, Nico Leidenfrost, Christine Zeh, Sascha Zemann}
+\author{\IEEEauthorblockN{Philip Trauner, Christoph Heiss}
 \IEEEauthorblockA{Department for Computer Science\\
@@
 Wiener Neustadt, Austria\\
-Email: philip.trauner@arztpraxis.io, me@christoph-heiss.me, se.schaffler@gmail.com, \\nico@nicokratky.me, leidenfrost.nico@gmail.com, zeh.chrisi@gmail.com, sascha.zemann@gmail.com}
+Email: philip.trauner@arztpraxis.io, me@christoph-heiss.me}
+Affiliated Authors: Sebastian Schaffler, Nico Kratky, Nico Leidenfrost, Christine Zeh, Sascha Zemann
 }
@@
 \section{Introduction}
-fl0w\cite{fl0w:Philip Trauner} was developed out of a need for a fast, reliable and wireless workflow solution that can compete with the currently available offerings like Harrogate\cite{Harrogate:KIPR}.
+fl0w\cite{fl0w:Philip Trauner} was developed out of the need for a fast, reliable and wireless workflow solution that can compete with the currently available offerings like Harrogate\cite{Harrogate:KIPR}.
 Its goals are to transform the connected controllers into a redundant fleet of logical units that share the same binaries and source code, real-time in-line sensor readouts, programming as well as robot management inside Sublime Text 3\cite{Sublime Text 3:Sublime HQ}, and a browser-based front-end.
@@
 \\All fl0w components are designed as libraries to allow for integration into other projects.
-fl0w utilities a client-server networking model with random server assignment.
-Client-server was chosen because the server can act as a data source for all clients.
+fl0w utilizes a client-server networking model with random server assignment.
+Client-server was chosen because the server can act as a data source for all clients and logic can be clearly separated.
 
@@
 Instead of one monolithic network protocol, undergr0und emphasizes small sub protocols.
-undergr0und manages itself through its own concepts.\\
+undergr0und manages itself through its own concepts by transmitting the initial handshake and metadata on a route.\\
 
@@
 undergr0und.js\cite{undergr0und.js:Philip Trauner} is the feature complete client-side JavaScript\cite{ECMAScript:Ecma} port of undergr0und\cite{undergr0und:Philip Trauner} that was required for dashb0ard\cite{dashb0ard:Sebastian Schaffler}, the browser-based front-end for fl0w\cite{fl0w:Philip Trauner}.
-\\It utilizes node-jspack\cite{node-jspack:Peter Griess} to unpack the binary messages it receives from the undergr0und server.
+It utilizes node-jspack\cite{node-jspack:Peter Griess} to unpack the binary messages it receives from the undergr0und server.
 It is based on the Python\cite{Python:Python Foundation} version but does not implement the server because there is currently no need for that functionality.
@@
 
-\subsubsection{Route}
+\subsubsection{Connection constructs}
+\paragraph{Route}
 A client$\,\to\,$server / server$\,\to\,$client construct. Invoked with the {\color{deepgreen}"send"} call.
 
-\subsubsection{Pipe}
+\paragraph{Pipe}
 A client$\,\to\,$server$\,\to\,$client construct.
@@
 Bray Ed.} is used to transfer lists and dictionaries, and regular ASCII encoded strings are utilized to transfer integers, floats, null/none types and strings.
-JSON was chosen because it can be serialized and parsed by Python\cite{Python:Python Foundation} as well as JavaScript\cite{ECMAScript:Ecma}.
 
@@
 behem0th\cite{behem0th:Christoph Heiss} neither sends nor receives files as a whole, instead it transmits the file as small blocks (4096 bytes), which are written to a temporary file on disk as soon as they are received.
-This is done to allow the transfer of large files even in very memory-constrained environments.\\
+This is done to allow the transfer of large files even in very random-access-memory-constrained environments.\\
 
@@
 
-\subsubsection{Security}
-Although MD5 is deprecated and known to suffers from extensive vulnerabilities, behem0th\cite{behem0th:Christoph Heiss} is designed to only run in a local network, which is controlled by the users of fl0w\cite{fl0w:Philip Trauner}.
+\subsubsection{Security concerns}
+Although MD5 is deprecated and known to suffer from extensive vulnerabilities, behem0th\cite{behem0th:Christoph Heiss} is designed to only run in a local network, which is controlled by the users of fl0w\cite{fl0w:Philip Trauner}.
 This assumption also simplifies the implementation greatly.
@@
 \subsection{dashb0ard}
-dashb0ard\cite{dashb0ard:Sebastian Schaffler} is a single-page web front-end designed to manage the fl0w\cite{fl0w:Philip Trauner} fleet.\\ It can be used to configure connected controllers and obtain sensor readouts as well as debug logs.
-\\It utilities undergr0und.js\cite{undergr0und.js:Philip Trauner} to retrieve data from fl0w, Vue.js\cite{Vue:Evan You} for its user interface, Bootstrap 3\cite{Bootstrap 3:Twitter Inc.} as a design baseline, Flot\cite{Flot:David Schnur} to display graphs and jQuery\cite{jQuery:jQuery Foundation} for additional DOM manipulation.
+dashb0ard\cite{dashb0ard:Sebastian Schaffler} is a single-page web application designed to manage the fl0w\cite{fl0w:Philip Trauner} fleet.\\ It can be used to configure connected controllers and obtain sensor readouts as well as debug logs.
+\\It utilizes undergr0und.js\cite{undergr0und.js:Philip Trauner} to retrieve data from fl0w, Vue.js\cite{Vue:Evan You} for its user interface, Bootstrap 3\cite{Bootstrap 3:Twitter Inc.} as a design baseline, Flot\cite{Flot:David Schnur} to display graphs and jQuery\cite{jQuery:jQuery Foundation} for additional DOM manipulation.
 
@@
 behem0th\cite{behem0th:Christoph Heiss} is embedded into edit0r and enables the source code synchronization.
-In its current form only C programs are supported.\\
+In its current form only C programs are supported because the folder structure for Python\cite{Python:Python Foundation} programs in Harrogate\cite{Harrogate:KIPR} is different.\\
 
@@
 \subsubsection{Robot management}
-Botball programs can be started (keyboard shortcut: F8) and/or stopped (keyboard shortcut: F9).
-Additionally, edit0r\cite{edit0r:Philip Trauner} allows for modification of the controller hostname, playback of a sound for identification purposes, listing of running processes, power management functionality (reboot, shutdown) and running programs.\\
+Botball programs can be started and/or stopped.
+Additionally, edit0r\cite{edit0r:Philip Trauner} allows for modification of the controller hostname, playback of a sound for identification purposes, listing of running processes, and power management functionality (reboot, shutdown).\\
 
 \subsubsection{In-line sensor readouts}
-Invocations of the functions "analog" and "digital" are located every time the content of a view changes and the parameters of the calls are grouped across views.
+Invocations of the functions "analog" and "digital", functions typically used to obtain sensor values, are located every time the content of a view changes and the parameters of the calls are grouped across views.
 edit0r\cite{edit0r:Philip Trauner} subscribes to all required sensor ports by requesting them from the currently selected controller.
 The controller keeps track of all subscriptions to sensors and continuously transmits the appropriate values to the Sublime Text 3\cite{Sublime Text 3:Sublime HQ} plugin.
-\\Sublime Text 3 phantoms are created as soon as new sensor values are available.
+\\Sublime Text 3 phantoms, which are in-line fields to display data within a text view, are created as soon as new sensor values are available.
 This approach has the disadvantage of higher than usual processor utilization by edit0r, because phantoms were primarily designed to display infrequently updating content.
 To partially circumvent this, sensor readouts can be disabled and are not enabled by default.\\
-In-line sensor readouts can be toggled on a per view basis with a keyboard shortcut (default F10).\\
+In-line sensor readouts can be toggled on a per view basis with a keyboard shortcut (default.\\
 
@@
 \section*{Acknowledgment}
-The authors would like to thank the robotics team robot0nfire: Nico Kratky, Nico Leidenfrost, Sebastian Schaffler, Christine Zeh, Sascha Zemann;\\ Dr.
-Michael Stifter for making the existence of our team possible; Daniel Maximilian Swoboda for answering all paper related questions; the KIPR development team without whom the Wallaby\cite{Wallaby Controller:KIPR} Controller would not exist.
+The authors would like to thank Dr.
+Michael Stifter for making the existence of our robotics team possible, Daniel Maximilian Swoboda for answering all paper related questions, and the KIPR development team without whom the Wallaby\cite{Wallaby Controller:KIPR} Controller would not exist.
 
@@
 
+\bibitem{dashb0ard:Sebastian Schaffler}
+Sebastian Schaffler, Philip Trauner, \emph{dashb0ard}, \url{https://github.com/robot0nfire/dashb0ard}, source code,
+accessed March 16th 2017
+
 \bibitem{undergr0und.js:Philip Trauner}
@@
 
+\bibitem{behem0th:Christoph Heiss}
+Christoph Heiss, \emph{behem0th}, \url{https://github.com/robot0nfire/behem0th},\\ source code,
+accessed February 9th 2017
+
 \bibitem{watchdog:Yesudeep Mangalapilly}
@@
 accessed March 22nd 2017
-
-\bibitem{dashb0ard:Sebastian Schaffler}
-Sebastian Schaffler, Philip Trauner, \emph{dashb0ard}, \url{https://github.com/robot0nfire/dashb0ard}, source code,
-accessed March 16th 2017
 
@@
 
-\bibitem{behem0th:Christoph Heiss}
-Christoph Heiss, \emph{behem0th}, \url{https://github.com/robot0nfire/behem0th},\\ source code,
-accessed February 9th 2017
-
 \end{thebibliography}

### 2017-04-02 paper.tex
Reverted Affiliated Authors

@@
 \title{fl0w - a development environment for the\\ KIPR Wallaby}
-\author{\IEEEauthorblockN{Philip Trauner, Christoph Heiss}
+\author{\IEEEauthorblockN{Philip Trauner, Christoph Heiss, Sebastian Schaffler, Nico Kratky, Nico Leidenfrost, Christine Zeh, Sascha Zemann}
 \IEEEauthorblockA{Department for Computer Science\\
@@
 Wiener Neustadt, Austria\\
-Email: philip.trauner@arztpraxis.io, me@christoph-heiss.me}
-Affiliated Authors: Sebastian Schaffler, Nico Kratky, Nico Leidenfrost, Christine Zeh, Sascha Zemann
+Email: philip.trauner@arztpraxis.io, me@christoph-heiss.me, se.schaffler@gmail.com, \\nico@nicokratky.me, leidenfrost.nico@gmail.com, zeh.chrisi@gmail.com, sascha.zemann@gmail.com}
 }

### 2017-04-16 paper.tex
Implemented suggested improvements by PRIA reviewers
* Removed unneeded citations
* Added first sentence of III -> G -> fl0w to implementation
* Properly removed reference to keyboard shortcuts
* Design considerations:
        * undergr0und already uses UTF-8 encoded strings, I'm just too stupid to know what the functions I use actually do
        * There is a back-off time in disc0very, I just forgot to mention it

@@
 \section{Implementation}
-All fl0w\cite{fl0w:Philip Trauner} components emphasize shared code and are therefor written in Python\cite{Python:Python Foundation} 3.3.6 to remain compatible with the Sublime Text 3\cite{Sublime Text 3:Sublime HQ} plugin environment.
-\\Python was chosen as the implementation language for fl0w because of its rich standard library and its lightweight virtual machine that can run on a Wallaby\cite{Wallaby Controller:KIPR} controller with acceptable speed.
+fl0w is the combination of all its components split into Wallaby\cite{Wallaby Controller:KIPR} client and server.
+All components emphasize shared code and are therefor written in Python\cite{Python:Python Foundation} 3.3.6 to remain compatible with the Sublime Text 3 plugin environment.
+\\Python was chosen as the implementation language for fl0w because of its rich standard library and its lightweight virtual machine that can run on a Wallaby controller with acceptable speed.
 A pre-compiled version of Python is bundled with the fl0w installer, r0adrunner, because it is not present on the Wallaby by default.
@@
 
-The Python\cite{Python:Python Foundation} version is built on top of a fork of ws4py\cite{ws4py:Philip Trauner} and the JavaScript\cite{ECMAScript:Ecma} version utilizes regular WebSockets\cite{The WebSocket Protocol:A.
+The Python version is built on top of a fork of ws4py\cite{ws4py:Philip Trauner} and the JavaScript\cite{ECMAScript:Ecma} version utilizes regular WebSockets\cite{The WebSocket Protocol:A.
 Melnikov} in arraybuffer mode.
-It was created because the requirements for fl0ws\cite{fl0w:Philip Trauner} network protocol specification changed constantly and a dynamic approach to networking was required.
+It was created because the requirements for fl0ws network protocol specification changed constantly and a dynamic approach to networking was required.
 Instead of one monolithic network protocol, undergr0und emphasizes small sub protocols.
@@
 \subsubsection{undergr0und.js}
-undergr0und.js\cite{undergr0und.js:Philip Trauner} is the feature complete client-side JavaScript\cite{ECMAScript:Ecma} port of undergr0und\cite{undergr0und:Philip Trauner} that was required for dashb0ard\cite{dashb0ard:Sebastian Schaffler}, the browser-based front-end for fl0w\cite{fl0w:Philip Trauner}.
+undergr0und.js\cite{undergr0und.js:Philip Trauner} is the feature complete client-side JavaScript port of undergr0und that was required for dashb0ard\cite{dashb0ard:Sebastian Schaffler}, the browser-based front-end for fl0w.
 It utilizes node-jspack\cite{node-jspack:Peter Griess} to unpack the binary messages it receives from the undergr0und server.
-It is based on the Python\cite{Python:Python Foundation} version but does not implement the server because there is currently no need for that functionality.
-\\undergr0und.js can be used in Node.js\cite{Node.js:Node.js Foundation} as well as browsers that support WebSockets\cite{The WebSocket Protocol:A.
-Melnikov}.
+It is based on the Python version but does not implement the server because there is currently no need for that functionality.
+\\undergr0und.js can be used in Node.js\cite{Node.js:Node.js Foundation} as well as browsers that support WebSockets.
 browserify\cite{browserify:James Halliday} is used to create the browser version.\\
@@
 \\Clients can be targeted with unique IDs that are generated randomly for all connected peers by the server.
-There is no predefined mechanism in the network protocol that exposed these peer IDs, the application using undergr0und\cite{undergr0und:Philip Trauner} has to provide a way of making them available.
+There is no predefined mechanism in the network protocol that exposed these peer IDs, the application using undergr0und has to provide a way of making them available.
 This approach allows for more flexibility if additional peer-metadata has to be provided.
@@
 JSON\cite{JSON:T.
-Bray Ed.} is used to transfer lists and dictionaries, and regular ASCII encoded strings are utilized to transfer integers, floats, null/none types and strings.
+Bray Ed.} is used to transfer lists and dictionaries, and regular UTF-8 encoded strings are utilized to transfer integers, floats, null/none types and strings.
 
 \subsection{behem0th}
-behem0th\cite{behem0th:Christoph Heiss} is a continuous network file synchronization protocol developed out of the need for an embeddable solution that would not require an additional background program to be present on the system running Sublime Text 3\cite{Sublime Text 3:Sublime HQ}, instead utilizing its plugin environment.
+behem0th\cite{behem0th:Christoph Heiss} is a continuous network file synchronization protocol developed out of the need for an embeddable solution that would not require an additional background program to be present on the system running Sublime Text 3, instead utilizing its plugin environment.
 \\It uses a client-server networking model without peer-to-peer capabilities to stay in line with undergr0und.
-It uses regular sockets instead of WebSockets\cite{The WebSocket Protocol:A.
-Melnikov} because the in-browser components of fl0w\cite{fl0w:Philip Trauner} never interacts with it.
+It uses regular sockets instead of WebSockets because the in-browser components of fl0w never interacts with it.
 The file-system is monitored using the watchdog\cite{watchdog:Yesudeep Mangalapilly} library.\\
@@
 \subsubsection{Synchronization}
-On startup, behem0th\cite{behem0th:Christoph Heiss} synchronizes files based on their last modification time and MD5 hash.
+On startup, behem0th synchronizes files based on their last modification time and MD5 hash.
 After that, files get synchronized to other clients as soon as a file-system event happens.
@@
 \subsubsection{Transfer}
-behem0th\cite{behem0th:Christoph Heiss} neither sends nor receives files as a whole, instead it transmits the file as small blocks (4096 bytes), which are written to a temporary file on disk as soon as they are received.
+behem0th neither sends nor receives files as a whole, instead it transmits the file as small blocks (4096 bytes), which are written to a temporary file on disk as soon as they are received.
 This is done to allow the transfer of large files even in very random-access-memory-constrained environments.\\
@@
 \subsubsection{Protocol}
-behem0th\cite{behem0th:Christoph Heiss} is independent from underg0und and defines its own network protocol.
-It is completely text-based, uses UTF-8 for character encoding and JSON\cite{JSON:T.
-Bray Ed.} as format encoding.
+behem0th is independent from undergr0und and defines its own network protocol.
+It is completely text-based, uses UTF-8 for character encoding and JSON as format encoding.
 behem0th is designed around 'requests' $($see Figure ~\ref{fig:behem0th_request}$)$ and 'routes'.
@@
 \end{json}
-\caption{behem0th request encoding in JSON\cite{JSON:T. Bray Ed.}}
+\caption{behem0th request encoding in JSON}
 \label{fig:behem0th_request}
@@
 \subsubsection{Security concerns}
-Although MD5 is deprecated and known to suffer from extensive vulnerabilities, behem0th\cite{behem0th:Christoph Heiss} is designed to only run in a local network, which is controlled by the users of fl0w\cite{fl0w:Philip Trauner}.
-This assumption also simplifies the implementation greatly.
+Although MD5 is deprecated and known to suffer from extensive vulnerabilities, behem0th is designed to only run in a local network, which is controlled by the users of fl0w This assumption also simplifies the implementation greatly.
 
 \subsection{dashb0ard}
-dashb0ard\cite{dashb0ard:Sebastian Schaffler} is a single-page web application designed to manage the fl0w\cite{fl0w:Philip Trauner} fleet.\\ It can be used to configure connected controllers and obtain sensor readouts as well as debug logs.
-\\It utilizes undergr0und.js\cite{undergr0und.js:Philip Trauner} to retrieve data from fl0w, Vue.js\cite{Vue:Evan You} for its user interface, Bootstrap 3\cite{Bootstrap 3:Twitter Inc.} as a design baseline, Flot\cite{Flot:David Schnur} to display graphs and jQuery\cite{jQuery:jQuery Foundation} for additional DOM manipulation.
+dashb0ard\cite{dashb0ard:Sebastian Schaffler} is a single-page web application designed to manage the fl0w fleet.\\ It can be used to configure connected controllers and obtain sensor readouts as well as debug logs.
+\\It utilizes undergr0und.js to retrieve data from fl0w, Vue.js\cite{Vue:Evan You} for its user interface, Bootstrap 3\cite{Bootstrap 3:Twitter Inc.} as a design baseline, Flot\cite{Flot:David Schnur} to display graphs and jQuery\cite{jQuery:jQuery Foundation} for additional DOM manipulation.
 
@@
 \includegraphics[scale=0.3]{dashb0ard}
-\caption{The control and configuration page of dashb0ard\cite{Sublime Text 3:Sublime HQ}}
+\caption{The control and configuration page of dashb0ard}
 \label{fig:dashb0ard_config}
@@
 \includegraphics[scale=0.25]{dashb0ard-sensor}
-\caption{The sensor readout page of dashb0ard\cite{Sublime Text 3:Sublime HQ}}
+\caption{The sensor readout page of dashb0ard}
 \label{fig:dashb0ard_sensor}
@@
 \subsection{edit0r}
-edit0r\cite{edit0r:Philip Trauner} is the Sublime Text 3\cite{Sublime Text 3:Sublime HQ} plugin.
-It is modeled as a fl0w\cite{fl0w:Philip Trauner} client and allows for remote robot management, source code synchronization as well as in-line sensor readouts.
-\\It also provides quick access to dashb0ard\cite{dashb0ard:Sebastian Schaffler}, which is required because the IP addresses of controllers are not always static.
-behem0th\cite{behem0th:Christoph Heiss} is embedded into edit0r and enables the source code synchronization.
-In its current form only C programs are supported because the folder structure for Python\cite{Python:Python Foundation} programs in Harrogate\cite{Harrogate:KIPR} is different.\\
+edit0r\cite{edit0r:Philip Trauner} is the Sublime Text 3 plugin.
+It is modeled as a fl0w client and allows for remote robot management, source code synchronization as well as in-line sensor readouts.
+\\It also provides quick access to dashb0ard, which is required because the IP addresses of controllers are not always static.
+behem0th is embedded into edit0r and enables the source code synchronization.
+In its current form only C programs are supported because the folder structure for Python programs in Harrogate is different.\\
 
 \subsubsection{Robot selection}
-fl0ws\cite{fl0w:Philip Trauner} networking model allows for the management of multiple controllers without a direct connection to them.
-The controller hostname is utilised to identify the robots in the user-interface.
+fl0ws networking model allows for the management of multiple controllers without a direct connection to them.
+The controller hostname is utilized to identify the robots in the user-interface.
 Controllers can be selected to obtain additional functionality such as in-line sensor readouts and keyboard shortcuts.\\
@@
 \includegraphics[scale=0.6]{edit0r}
-\caption{edit0rs\cite{edit0r:Philip Trauner} robot management interface in Sublime Text 3\cite{Sublime Text 3:Sublime HQ}}
+\caption{edit0rs robot management interface in Sublime Text 3}
 \label{fig:robot_management}
@@
 Botball programs can be started and/or stopped.
-Additionally, edit0r\cite{edit0r:Philip Trauner} allows for modification of the controller hostname, playback of a sound for identification purposes, listing of running processes, and power management functionality (reboot, shutdown).\\
+Additionally, edit0r allows for modification of the controller hostname, playback of a sound for identification purposes, listing of running processes, and power management functionality (reboot, shutdown).\\
 
@@
 Invocations of the functions "analog" and "digital", functions typically used to obtain sensor values, are located every time the content of a view changes and the parameters of the calls are grouped across views.
-edit0r\cite{edit0r:Philip Trauner} subscribes to all required sensor ports by requesting them from the currently selected controller.
-The controller keeps track of all subscriptions to sensors and continuously transmits the appropriate values to the Sublime Text 3\cite{Sublime Text 3:Sublime HQ} plugin.
+edit0r subscribes to all required sensor ports by requesting them from the currently selected controller.
+The controller keeps track of all subscriptions to sensors and continuously transmits the appropriate values to the Sublime Text 3 plugin.
 \\Sublime Text 3 phantoms, which are in-line fields to display data within a text view, are created as soon as new sensor values are available.
@@
 To partially circumvent this, sensor readouts can be disabled and are not enabled by default.\\
-In-line sensor readouts can be toggled on a per view basis with a keyboard shortcut (default.\\
+In-line sensor readouts can be toggled on a per view basis with a keyboard shortcut.\\
 
@@
 \includegraphics[scale=0.7]{sensor-readouts}
-\caption{edit0rs\cite{edit0r:Philip Trauner} inline sensor-readouts in Sublime Text 3\cite{Sublime Text 3:Sublime HQ}}
+\caption{edit0rs inline sensor-readouts in Sublime Text 3}
 \label{fig:inline_sensor_readouts}
@@
 \subsection{r0adrunner}
-r0adrunner is the installer of fl0w\cite{fl0w:Philip Trauner}.
-\\It is built to mimic a Wallaby\cite{Wallaby Controller:KIPR} controller software update to remain compatible with the preexisting update functionality found in Harrogate\cite{Harrogate:KIPR}.
-It is implemented in Python\cite{Python:Python Foundation} 2.7, which is already installed on all Wallaby controllers.
+r0adrunner is the installer of fl0w.
+\\It is built to mimic a Wallaby controller software update to remain compatible with the preexisting update functionality found in Harrogate.
+It is implemented in Python 2.7, which is already installed on all Wallaby controllers.
 A full-fledged precompiled version of Python 3.6.0 is installed by r0adrunner because fl0w utilizes features of Python 3.3.6.
@@
 \subsection{disc0very}
-disc0very\cite{disc0very:Christoph Heiss} is the LAN discovery protocol of fl0w\cite{fl0w:Philip Trauner}.
+disc0very\cite{disc0very:Christoph Heiss} is the LAN discovery protocol of fl0w.
 It relies on UDP\cite{UDP:J.
 Postel} broadcasts to coordinate server and client assignment.
-Wallaby controller instances as well as the Sublime Text 3\cite{Sublime Text 3:Sublime HQ} plugin edit0r\cite{edit0r:Philip Trauner} make use of it to determine if there is already an active fl0w server on the network upon startup without user interaction.
+Wallaby controller instances as well as the Sublime Text 3 plugin edit0r make use of it to determine if there is already an active fl0w server on the network upon startup without user interaction.
 
 \subsubsection{Discovery process}
-Upon launch disc0very\cite{disc0very:Christoph Heiss} listens for advertisements from an already running fl0w\cite{fl0w:Philip Trauner} server.
+Upon launch disc0very listens for advertisements from an already running fl0w server.
 If an advertisement is received the client-mode is engaged and a connection to the server is established.
@@
 \end{json}
-\caption{disc0very\cite{disc0very:Christoph Heiss} advertisement encoding in JSON\cite{JSON:T. Bray Ed.}}
+\caption{disc0very advertisement encoding in JSON\cite{JSON:T. Bray Ed.}}
 \label{fig:discovery_advertisement}
@@
 \subsubsection{Error recovery}
-disc0very\cite{disc0very:Christoph Heiss} actively listens for advertisements in server-mode to prevent more than one running server on the network.
-If a server receives an advertisement from another server both shutdown and return to discovery mode.
+disc0very actively listens for advertisements in server-mode to prevent more than one running server on the network.
+If a server receives an advertisement from another server both shut down, wait for a random amount of time (between 1 and 5 seconds), and return to discovery mode.
 
 \subsection{fl0w}
-fl0w\cite{fl0w:Philip Trauner} itself is the combination of all other components split into Wallaby\cite{Wallaby Controller:KIPR} client and server.\\
+fl0w itself is the combination of all other components split into Wallaby client and server.\\
 
 \subsubsection{Wallaby client}
-The Wallaby\cite{Wallaby Controller:KIPR} client serves as an information source for sensor values, program output, as well as currently running processes.
+The Wallaby\ client serves as an information source for sensor values, program output, as well as currently running processes.
 Additionally it exposes its own standard output for monitoring purposes.\\
@@
 The server keeps track of all clients and provides means to acquire their peer IDs, which are used by undergr0und to target specific clients.
-Additionally it serves dashb0ard\cite{dashb0ard:Sebastian Schaffler} and handles program compilation.
-It utilizes undergr0und for networking, behem0th for file-synchronization, and disc0very\cite{disc0very:Christoph Heiss} to determine if another server is already running in the network.
+Additionally it serves dashb0ard and handles program compilation.
+It utilizes undergr0und for networking, behem0th for file-synchronization, and disc0very to determine if another server is already running in the network.
 \\
-In that situation the start is interrupted, the Wallaby\cite{Wallaby Controller:KIPR} client is started and it connects to the available server instance, otherwise server and client are started. \\
+In that situation the start is interrupted, the Wallaby client is started and it connects to the available server instance, otherwise server and client are started. \\
 
 \section{Conclusion}
-After prolonged testing it was deemed reasonable to claim that fl0w\cite{fl0w:Philip Trauner} can improve the Botball development work-flow on Wallaby\cite{Wallaby Controller:KIPR} controllers.
+After prolonged testing it was deemed reasonable to claim that fl0w can improve the Botball development work-flow on Wallaby controllers.
 Experienced Botball teams that would rather program in native tools than the browser-based Harrogate and want to observe their sensor-readouts in realtime can benefit from fl0w.
@@
 
-Support for Python\cite{Python:Python Foundation} as a robot programming language as well as basic remote procedure call functionality is the next development goal.
+Support for Python as a robot programming language as well as basic remote procedure call functionality is the next development goal.
 
@@
 The authors would like to thank Dr.
-Michael Stifter for making the existence of our robotics team possible, Daniel Maximilian Swoboda for answering all paper related questions, and the KIPR development team without whom the Wallaby\cite{Wallaby Controller:KIPR} Controller would not exist.
+Michael Stifter for making the existence of our robotics team possible, Daniel Maximilian Swoboda for answering all paper related questions, and the KIPR development team without whom the Wallaby Controller would not exist.
 
@@
 
+\bibitem{Wallaby Controller:KIPR}
+KIPR, \emph{Wallaby Controller},\\  \url{http://botballstore.org/product/wallaby-controller}, store page, accessed February 9th 2017
+
 \bibitem{Python:Python Foundation}
@@
 accessed February 9th 2017
-
-\bibitem{Wallaby Controller:KIPR}
-KIPR, \emph{Wallaby Controller},\\  \url{http://botballstore.org/product/wallaby-controller}, store page, accessed February 9th 2017
 
@@
 
+\bibitem{undergr0und.js:Philip Trauner}
+Philip Trauner, \emph{undergr0und},\\ \url{https://github.com/robot0nfire/undergr0und.js}, source code, \\accessed February 9th 2017
+
 \bibitem{dashb0ard:Sebastian Schaffler}
@@
 accessed March 16th 2017
-
-\bibitem{undergr0und.js:Philip Trauner}
-Philip Trauner, \emph{undergr0und},\\ \url{https://github.com/robot0nfire/undergr0und.js}, source code, \\accessed February 9th 2017
 
